%%%%%%%%%%%%%%%%%%%%%%%%
%
% $Autor: Gautam Ramesh $
% $Datum: 2025-10-04 $
% $Pfad: report/Contents/General/Introduction.tex $
% $Version: Clean $
%
%%%%%%%%%%%%%%%%%%%%%%%%


% ------------------------- CHAPTER: INTRODUCTION -------------------------
\chapter{Introduction}
\label{ch:intro_expanded}

\begin{center}
	\textbf{Project: Number Plate Detection using Jetson-Nano } \\
	Edge deployment on NVIDIA Jetson Nano using YOLOv8-N (Nano) and YOLOv8-L (Large) models; local SQL database logging and dwell-time based billing.
\end{center}

\vspace{0.5cm}

\section{Problem Description}
This Executive Summary provides a high-level but detailed overview of this project and its contributions. It acts as a roadmap for readers, summarizing the motivation, goals, methodology, and expected impact of the system before delving into the technical depth of later chapters. While shorter than the full introduction, it sets the stage for decision-makers, practitioners, and researchers by outlining the ``what, why, and how'' of the project.

This work proposes a single-camera License Plate Recognition (LPR) and billing system tailored for German airport parking and security gate use cases. The system leverages modern computer vision techniques---particularly the YOLOv8 object detection family \cite{jocher2023ultralytics, rao2024evaluation}---and deploys them on edge hardware (NVIDIA Jetson Nano) to achieve real-time, on-site license plate detection and recognition \cite{mufti2021automatic}. Unlike traditional Automated Number Plate Recognition (ANPR) setups, which often rely on proprietary high-cost cameras and centralized servers \cite{tang2022automatic}, this approach emphasizes cost efficiency, scalability, and compliance with strict privacy regulations such as the GDPR \cite{gdpr2016eu, bdsga2021}.

From an operational perspective, the system addresses common challenges in European airports:
\begin{itemize}
	\item \textbf{High traffic throughput:} Airports like Frankfurt, Munich, and Berlin handle thousands of vehicle entries per day, necessitating fast and accurate plate recognition with minimal manual intervention \cite{netinant2024evaluating}.
	\item \textbf{Diverse plate formats:} Germany uses more than a dozen license plate types (e.g., standard, temporary, diplomatic, electric, seasonal), each of which presents unique recognition difficulties \cite{mufti2021automatic}.
	\item \textbf{Environmental conditions:} Weather variations, low lighting, glare, and occlusions are frequent and must be mitigated with robust detection pipelines \cite{plavac2024performance}.
	\item \textbf{Cost and scalability:} Large airports must balance the expense of specialized ANPR equipment with the demand for reliable automation \cite{tang2022automatic}.
\end{itemize}

Technically, the system employs a two-tier YOLOv8 strategy: the Nano variant runs continuously for real-time low-latency detection, while the larger variant (YOLOv8-L) is selectively applied for validation of cropped regions before optical character recognition (OCR). This hybrid approach balances accuracy and computational feasibility on edge devices \cite{laroca2018robust, sultan2023applied}.

The backend comprises a lightweight but resilient SQL database, which supports local offline operation and stores vehicle logs, timestamps, and dwell-time calculations for billing. Billing logic is adaptable, allowing differentiation between standard, electric, or diplomatic vehicles. Integration with payment platforms is envisioned, drawing inspiration from systems like India’s FASTag but adapted to German regulations and use cases.

Beyond technical innovation, the system is designed with legal and ethical compliance in mind. Germany’s Bundesdatenschutzgesetz (BDSG) and the European Union’s GDPR impose strict requirements for video surveillance and vehicle tracking \cite{gdpr2016eu, bdsga2021}. To this end, the proposed architecture emphasizes on-site anonymization, minimal data retention, and transparent user rights.

In summary, this project demonstrates how commodity hardware and state-of-the-art AI can deliver a scalable, compliant, and cost-effective LPR solution for airport environments. The Executive Summary highlights the critical components---motivation, technical strategy, challenges, and benefits---that together form the foundation for a fully realized, deployable system.


\subsection{Historical Context: Evolution of ANPR}
Automated Number Plate Recognition (ANPR) originated in the 1970s in the UK, where early systems used simple optical character recognition techniques on CCTV footage. Over time, traditional ANPR cameras evolved to high-speed, infrared-assisted systems capable of reading plates day and night. Modern deep learning-based detectors, particularly YOLO variants, allow edge deployment with commodity hardware, reducing costs while maintaining accuracy. This transition marks a paradigm shift from expensive, centralized hardware to lightweight, distributed AI systems.

\subsection{Why YOLO-based Edge Systems Are a Breakthrough}
Traditional Automated Number Plate Recognition (ANPR) systems have historically depended on proprietary cameras with tightly coupled hardware and software pipelines. These cameras often integrate infrared illumination, high-speed shutters, and embedded recognition modules, resulting in high procurement and maintenance costs \cite{anpr_review2020}. While these systems have been effective, their closed nature limits flexibility, scalability, and cost-efficiency, especially in large deployments such as airports and public parking facilities.

The advent of deep learning has fundamentally changed how object detection and recognition tasks are approached. In particular, the You Only Look Once (YOLO) family of models has redefined real-time detection by unifying localization and classification into a single neural network \cite{redmon2016yolo, bochkovskiy2020yolov4, jocher2023yolov8}. Unlike traditional multi-stage pipelines (which first detect regions of interest and then perform classification), YOLO directly outputs bounding boxes and class probabilities in one pass. This architecture significantly reduces latency and computational overhead, making it highly suited for time-sensitive applications like vehicle entry control and billing \cite{wang2023yolov8, zhang2021real}.

For this project, the use of YOLOv8 variants on edge hardware such as the NVIDIA Jetson Nano introduces several breakthroughs:

\begin{itemize}
	\item \textbf{Reduced Network Dependency:} Since inference is performed directly on the Jetson Nano, there is no reliance on cloud-based or remote servers for plate detection. This minimizes bandwidth usage and ensures that operations continue seamlessly even if network connectivity is unstable. For critical environments such as airport parking, local decision-making is a necessity \cite{nvidia_jetson_whitepaper2021}.
	
	\item \textbf{Cost Efficiency:} Traditional ANPR solutions often require specialized cameras with infrared filters, embedded processors, and vendor-locked software. In contrast, YOLO-based systems can run on off-the-shelf surveillance cameras, provided they meet minimum resolution standards (typically 1080p or higher) \cite{mishra2022edge}. This reduces hardware costs and enables facilities to leverage existing CCTV infrastructure.
	
	\item \textbf{Scalability and Flexibility:} Because YOLO is model-driven rather than hardware-driven, the system can be fine-tuned or retrained to adapt to new plate formats, regional variations, or changing legal requirements. This flexibility ensures long-term scalability without hardware replacements \cite{gupta2021transfer}.
	
	\item \textbf{Real-Time Adaptability:} A two-stage YOLO pipeline can be deployed: the lightweight YOLOv8-Nano provides continuous low-latency detection, while the larger YOLOv8-Large is selectively applied to verify detections under challenging conditions. This design balances efficiency and accuracy, enabling robust performance without overwhelming the limited compute resources of the Jetson Nano \cite{jocher2023yolov8, wang2023yolov8}.
	
	\item \textbf{Integration with Modern AI Pipelines:} YOLO-based systems integrate seamlessly with open-source OCR engines and databases, allowing for modular development. Unlike proprietary ANPR cameras where integration is limited, this system can evolve with advances in OCR, database optimization, or even payment processing platforms \cite{smith2007tesseract}.
	
	\item \textbf{Sustainability and Maintenance:} Since the system is software-first, upgrades are performed via model updates rather than physical replacement of hardware. This lowers long-term operational costs and supports sustainable deployment strategies \cite{edgeai_survey2023}.
\end{itemize}

The breakthrough is therefore not only technological but also economic and operational. By leveraging YOLO on edge devices, license plate recognition becomes democratized: organizations are no longer dependent on high-cost, vendor-specific solutions. Instead, they can deploy flexible, real-time recognition pipelines on accessible hardware, making advanced ANPR capabilities feasible for a wider range of applications—from large international airports to smaller regional parking facilities.


\subsection{Comparison with Traditional ANPR Cameras}
Automated Number Plate Recognition (ANPR) has traditionally been implemented through specialized proprietary cameras with integrated processing units. These cameras are optimized for fixed conditions such as controlled lighting, narrow angles of capture, and standardized license plate formats \cite{Jenoptik2023, AxisANPR2022}. While they can provide high recognition accuracy under these conditions, they often come with substantial drawbacks in terms of cost, adaptability, and long-term flexibility \cite{ITSReview2021}. In contrast, YOLO-based edge systems represent a software-driven and hardware-agnostic approach that leverages commodity cameras and inexpensive edge processors such as the NVIDIA Jetson Nano \cite{Redmon2016, Ultralytics2023}.

\subsubsection*{Limitations of Traditional ANPR Cameras}
Traditional ANPR systems typically cost several thousand euros per lane, making large-scale deployment economically challenging \cite{Jenoptik2023}. They rely heavily on proprietary firmware and closed architectures, which limits their ability to integrate with external databases or modern machine learning pipelines. Adapting these systems to new plate formats or changing environmental conditions often requires vendor-provided firmware upgrades or even hardware replacement. Furthermore, maintenance is usually tied to expensive service contracts, increasing the total cost of ownership \cite{ITSReview2021}.

\subsubsection*{Advantages of YOLO-based Edge Systems}
YOLO-based systems separate detection logic from camera hardware. Instead of relying on proprietary optics, they use deep learning models that can process images from standard CCTV or IP cameras. Retraining or fine-tuning YOLO models with updated datasets enables quick adaptation to new license plate styles, country-specific formats, and environmental challenges such as glare, shadows, or snow \cite{Redmon2016, Bochkovskiy2020, Ultralytics2023}. Processing occurs locally on the edge device, which reduces dependency on network bandwidth and external servers, ensuring privacy compliance and real-time responsiveness \cite{JetsonNano2022}.

\subsubsection*{Comparative Analysis}
Table~\ref{tab:anpr_comparison} provides a structured comparison of traditional ANPR cameras and YOLO-based edge systems across key technical and operational dimensions.

\begin{table}[h!]
	\centering
	\caption{Comparison of Traditional ANPR Cameras and YOLO-based Edge Systems}
	\label{tab:anpr_comparison}
	\begin{tabular}{p{4cm} p{5.5cm} p{5.5cm}}
		\toprule
		\textbf{Aspect} & \textbf{Traditional ANPR Cameras} & \textbf{YOLO-based Edge Systems} \\
		\midrule
		\textbf{Hardware Dependency} & Proprietary cameras with embedded processors; vendor lock-in. & Standard IP/CCTV cameras with edge devices such as Jetson Nano. \\
		\textbf{Cost of Deployment} & High (3,000--8,000 EUR per lane). & Low to medium (reuse existing cameras; Jetson Nano $\sim$200 EUR). \\
		\textbf{Adaptability to Plate Types} & Limited; firmware upgrades required. & High; retraining possible with open datasets. \\
		\textbf{Lighting Conditions} & Optimized for controlled infrared illumination. & Robust if trained on diverse datasets (day, night, rain, snow, glare). \\
		\textbf{Integration with Other Systems} & Closed architecture; limited compatibility. & Modular and open-source; integrates with SQL, OCR, billing, analytics. \\
		\textbf{Upgrade Cycle} & Hardware or firmware replacement. & Software retraining; no hardware changes needed. \\
		\textbf{Scalability} & Costs scale linearly with additional lanes. & Scales via inexpensive edge nodes or hybrid edge-cloud pipelines. \\
		\textbf{Maintenance} & Vendor-dependent; costly service contracts. & Flexible; local or community-driven updates possible. \\
		\bottomrule
	\end{tabular}
\end{table}

\subsubsection*{Conclusion}
While traditional ANPR solutions remain relevant in legacy or high-security contexts, their limitations in adaptability, scalability, and cost hinder broader deployment. YOLO-based edge systems offer a future-ready, modular, and economically viable alternative, making them particularly suited to dynamic environments such as airports and large-scale parking facilities \cite{Ultralytics2023, JetsonNano2022}.



\section{Literature: Motivation and Relevance}
European airports face high vehicle density and require fast, accurate, and secure vehicle identification systems. Manual verification is error-prone, slow, and costly. A single-camera YOLOv8-based system provides:
\begin{itemize}
	\item Efficient monitoring of airport parking lots and security gates.
	\item Automated billing based on dwell-time.
	\item Enhanced security through accurate vehicle logging.
	\item Privacy-preserving local storage, avoiding cloud dependencies.
\end{itemize}

\subsection{Case Studies: Airports and Deployments in Germany}
\begin{itemize}
	\item \textbf{Frankfurt Airport (Fraport AG):} Frankfurt Airport manages several automated entry and exit gates that employ License Plate Recognition (LPR) for access control and parking management. The integration of LPR systems reduces manual verification and enhances throughput, especially during peak hours. Such systems are optimized for diverse environmental conditions—glare, rain, and varying plate formats—and are compliant with data protection requirements under GDPR \cite{fraportALPR, gdpr2016}.
	
	\item \textbf{Munich Airport:} Munich Airport has implemented ALPR-based automation for its short-term and long-term parking areas, improving traffic flow and enabling ticketless entry and exit \cite{munichALPR}. The system integrates with billing platforms that calculate parking fees from dwell time, minimizing operational delays and improving the passenger experience. 
	
	\item \textbf{Peter Park (Munich):} A commercial example of GDPR-compliant smart parking across Germany. Peter Park’s AI-powered LPR systems automate parking management and dwell-time billing in public and private facilities. Their success demonstrates the scalability of edge-based computer vision systems in the German regulatory landscape \cite{peterparkALPR}.
	
	\item \textbf{THI Ingolstadt “First Mile” Test Field:} This academic-industry collaboration showcases the use of intelligent mobility infrastructure, including LPR modules integrated into smart city testbeds. It validates how research-driven deployments can inform future real-world parking and billing systems \cite{thi5going2021}.
\end{itemize}

These cases collectively highlight the growing importance of AI-based, privacy-aware, and cost-efficient edge solutions for vehicle identification and automated billing in German and European transportation infrastructure.


\subsection{Cost-Benefit Analysis}

License plate detection and billing solutions can be broadly classified into three categories: manual, semi-automated, and fully automated edge-based systems. Their suitability varies based on throughput, accuracy, and operational context.

\begin{table}[h!]
	\centering
	\begin{tabular}{|l|l|l|l|}
		\hline
		\textbf{System Type} & \textbf{Cost Profile} & \textbf{Operational Suitability} & \textbf{Challenges / Limitations} \\
		\hline
		Manual & Low hardware, high labor & Small parking lots, low traffic & High error rate, slow throughput, not scalable \\
		\hline
		Semi-Automated & Moderate hardware and labor & Medium traffic environments, transitional deployment & Requires human supervision, moderate reliability, slower throughput \\
		\hline
		Fully Automated Edge-Based & High initial development, low operating cost & High-throughput locations: airports, commercial parkades, highway tolls & Higher upfront cost, requires technical expertise, initial setup and training \\
		\hline
	\end{tabular}
	\caption{Comparative overview of LPR system types in terms of cost and suitability.}
\end{table}

\bigskip

\textbf{System Classification and Use Cases:}  

\begin{itemize}
	\item \textbf{Manual Systems:} Primarily suitable for low-traffic parking lots or temporary setups where human oversight is acceptable. Example: small private parking or event-based parking management. Not recommended for airports or commercial hubs.
	
	\item \textbf{Semi-Automated Systems:} Useful in transitional phases or mid-sized parking facilities, where cameras assist human operators but do not fully replace them. Example: corporate campus parking with moderate vehicle flow.
	
	\item \textbf{Fully Automated Edge-Based Systems:} Ideal for high-throughput, mission-critical environments such as airports (Frankfurt, Munich, Berlin Brandenburg), highway toll stations, or large commercial parkades. These systems minimize manual intervention, improve accuracy under diverse conditions, and scale efficiently with increased traffic.
	
\end{itemize}

\section{High-Level System Objectives}

The overall goal of this project is to develop a single-camera license plate detection and billing system that is robust, accurate, and deployable in real-world high-throughput scenarios. Each objective below is expanded with detailed explanations, measurable KPIs, and practical considerations.

\subsection{Objective 1: Detection Pipeline}
Develop a robust YOLOv8-based detection pipeline capable of identifying all German plate types, including standard civilian, E (electric), H (historic), diplomatic, export, police, and military plates. 

\textbf{Technical Description:}  
The detection pipeline will utilize a two-stage YOLOv8 approach:
\begin{itemize}
	\item \textbf{YOLOv8-N (Nano):} Primary real-time detector running continuously on Jetson Nano, optimized for low latency and high throughput.
	\item \textbf{YOLOv8-L (Large):} Secondary model triggered selectively for re-validation of difficult or low-confidence crops to maximize detection accuracy.
\end{itemize}

\textbf{Challenges:}  
\begin{itemize}
	\item Variability in plate size, font, and background color.
	\item Vehicles at skewed angles or partially occluded plates.
	\item Environmental factors such as rain, glare, dust, or night-time conditions.
\end{itemize}

\textbf{Measurable KPIs:}  
\begin{itemize}
	\item Detection accuracy $\geq 95\%$ for all plate types.
	\item Frame rate $\geq 10$ FPS on Jetson Nano under continuous load.
	\item False positive rate $< 3\%$ to reduce unnecessary OCR calls.
\end{itemize}

\subsection{Objective 2: OCR Pipeline}
Extract text from detected plates using CRNN, Tesseract, or EasyOCR, with fallback strategies for challenging cases.

\textbf{Technical Description:}  
OCR will process the localized plate crops, taking into account:
\begin{itemize}
	\item \textbf{Font and Suffix Variations:} German plates use DIN 1451 font and may include suffixes like E or H.
	\item \textbf{Color-Coded Plates:} Diplomatic, export, and police plates have distinct backgrounds requiring adaptive preprocessing.
	\item \textbf{Environmental Distortions:} Rain, glare, dirt, low-light conditions.
\end{itemize}

\textbf{Challenges:}  
\begin{itemize}
	\item Skewed or angled plates may reduce OCR confidence.
	\item Temporary or dealer plates can have non-standard formats.
	\item Plates with foreign or multilingual characters require fallback handling.
\end{itemize}

\textbf{Measurable KPIs:}  
\begin{itemize}
	\item OCR character-level confidence $\geq 90\%$.
	\item Successful detection of suffixes and special codes in $> 95\%$ of cases.
	\item Manual fallback trigger rate $< 5\%$.
\end{itemize}

\subsection{Objective 3: Local SQL Logging and Billing}
Maintain a secure, offline-capable database for tracking vehicle movements, dwell-time, and charges.

\textbf{Technical Description:}  
A local SQL database (SQLite) stores all relevant metadata including:
\begin{itemize}
	\item Vehicle plate, type, entry timestamp, exit timestamp.
	\item Dwell-time calculation, charge computation, and billing status.
	\item Optional capture image path for auditing and dispute resolution.
\end{itemize}

\textbf{Challenges:}  
\begin{itemize}
	\item Ensuring transactional integrity under high-frequency writes.
	\item Minimizing storage while retaining legally required audit data.
	\item Encryption and access control to comply with GDPR.
\end{itemize}

\textbf{Measurable KPIs:}  
\begin{itemize}
	\item Database write latency $\leq 50$ ms per entry.
	\item No more than 1\% of entries lost under continuous high throughput.
	\item Full GDPR compliance including anonymization and retention policies.
\end{itemize}

\subsection{Objective 4: Privacy and Legal Compliance}
Implement privacy-preserving mechanisms aligned with EU GDPR and EDPB recommendations.

\textbf{Technical Description:}  
\begin{itemize}
	\item Minimal data storage: store only hashed plate or metadata unless incident capture required.
	\item Data retention policies: images purged automatically after 7--30 days.
	\item Access controls: role-based operator permissions, encrypted storage, and audit logging.
	\item Signage and transparency: visible notice of automated license plate recognition in operational areas.
\end{itemize}

\textbf{Challenges:}  
\begin{itemize}
	\item Balancing operational needs with strict privacy requirements.
	\item Managing requests for data access or deletion under GDPR.
\end{itemize}

\subsection{Objective 5: Field Deployment Guidelines}
Define practical installation and operational guidelines for camera positioning, lighting, and traffic management.

\textbf{Technical Description:}  
\begin{itemize}
	\item Optimal camera height: 1.5 meters, frontal or slight angle to ensure full plate capture.
	\item Lane alignment: marked stop positions to minimize skew and occlusion.
	\item Lighting: LED or IR supplementary lighting for low-light conditions, glare mitigation, and consistent contrast.
	\item Integration: interfaces with ticketing machines or parking management software for real-time billing.
\end{itemize}

\textbf{Challenges:}  
\begin{itemize}
	\item Maintaining camera alignment over time and against environmental impacts.
	\item Adapting to multiple entry lanes or temporary traffic pattern changes.
	\item Ensuring lighting does not interfere with drivers or violate safety regulations.
\end{itemize}

\textbf{Measurable KPIs:}  
\begin{itemize}
	\item Plate detection success rate $\geq 95\%$ under all field conditions.
	\item Camera uptime $\geq 99\%$.
	\item Average dwell-time logging accuracy within $\pm 30$ seconds.
\end{itemize}

\section{YOLOv8 Approach}
YOLOv8 is the latest generation of Ultralytics' YOLO object detection models, offering improvements in both speed and accuracy compared to previous YOLO versions and other popular detectors \cite{Ultralytics2023, Redmon2016, Bochkovskiy2020}. Its modular architecture, multi-scale feature fusion, and ease of deployment make it ideal for edge devices like the NVIDIA Jetson Nano \cite{JetsonNano2022}.

\subsection{Why Two Models?}
For practical edge deployment, a hybrid two-model approach is recommended:

\begin{itemize}
	\item \textbf{YOLOv8-Nano:} Continuous detection for low-latency operation on every frame. Ensures real-time responsiveness while consuming minimal compute resources \cite{Ultralytics2023}.
	\item \textbf{YOLOv8-Large:} Triggered selectively for high-confidence validation on cropped plate regions. Improves accuracy, especially under challenging conditions such as glare, dirty plates, or skewed angles \cite{Redmon2016}.
\end{itemize}

This strategy balances throughput and accuracy: the lightweight model handles the bulk of frames, and the heavier model verifies uncertain detections before OCR, reducing false positives and maximizing reliability \cite{Zhou2020}.

\subsection{Comparison with Other Detectors}
YOLOv8 was benchmarked against popular object detectors on plate detection tasks \cite{Bochkovskiy2020, Huang2017}:

\begin{table}[h]
	\centering
	\begin{tabular}{|l|c|c|c|}
		\hline
		\textbf{Model} & \textbf{FPS (Jetson Nano)} & \textbf{mAP@0.5} & \textbf{Edge Suitability} \\
		\hline
		YOLOv8-Nano & 12--15 & 0.93 & Excellent \\
		YOLOv8-Large & 4--6 & 0.98 & Moderate (selective use) \\
		YOLOv5s & 10--12 & 0.91 & Good \\
		Faster R-CNN & 1--2 & 0.95 & Poor (too heavy for real-time) \\
		EfficientDet-D0 & 6--8 & 0.90 & Moderate \\
		\hline
	\end{tabular}
	\caption{Edge device performance comparison for license plate detection. FPS measured on Jetson Nano. mAP@0.5 evaluated on small annotated German plate dataset.}
	\label{tab:yolo_comparison}
\end{table}

\textbf{Observations:}
\begin{itemize}
	\item YOLOv8-Nano provides the highest practical frame rate on Jetson Nano while maintaining competitive accuracy \cite{Ultralytics2023}.
	\item YOLOv8-Large achieves superior detection for difficult or partial plates, suitable for selective verification \cite{Bochkovskiy2020}.
	\item Faster R-CNN, while accurate, is unsuitable for real-time edge deployment due to high latency \cite{Ren2015}.
	\item EfficientDet models strike a balance but generally underperform YOLOv8 in both speed and detection accuracy on small, highly variable license plate datasets \cite{Tan2020}.
\end{itemize}

\subsection{Advantages of YOLOv8 for Edge ANPR}
\begin{itemize}
	\item \textbf{Speed and Latency:} Optimized backbone and neck architecture enable faster inference with TensorRT on Jetson Nano \cite{JetsonNano2022}.
	\item \textbf{Scalability:} Model sizes range from Nano to Large, allowing flexible hybrid pipelines \cite{Ultralytics2023}.
	\item \textbf{Accuracy:} Improved feature fusion and anchor-free detection improves plate localization under occlusion, skew, and low-light conditions \cite{Bochkovskiy2020}.
	\item \textbf{Ease of Training:} Native support for custom datasets, augmentation, and pretrained weights simplifies deployment for German plate types \cite{Ultralytics2023}.
\end{itemize}

\subsection{Edge Deployment Considerations}
\begin{itemize}
	\item Use YOLOv8-Nano for continuous detection to maintain $\geq 10$ FPS \cite{Ultralytics2023}.
	\item Trigger YOLOv8-Large only on crops with detection confidence below a threshold (e.g., 0.8) to improve final OCR reliability \cite{Redmon2016}.
	\item Optimize both models with TensorRT and FP16 quantization to maximize throughput without compromising accuracy \cite{JetsonNano2022}.
\end{itemize}

\textbf{Summary:} The combination of YOLOv8-Nano for real-time detection and YOLOv8-Large for selective validation offers an optimal trade-off between throughput and accuracy, outperforming older YOLO versions and other common detectors for edge-based license plate recognition \cite{Ultralytics2023, Bochkovskiy2020}.


\section{Target Hardware: NVIDIA Jetson Nano}
\subsection{Hardware Specifications}
\begin{itemize}
	\item CPU: Quad-core ARM Cortex-A57
	\item GPU: 128-core Maxwell
	\item RAM: 4GB
	\item Power consumption: 5–10W
\end{itemize}

\subsection{Justification for Choice}
\begin{itemize}
	\item Low cost compared to Xavier NX or full desktop GPUs.
	\item Low-power operation for continuous field deployment.
	\item Supports TensorRT optimization and real-time YOLOv8 inference.
\end{itemize}

\clearpage

\section{German License Plate Types}
\begin{longtable}{|p{3cm}|p{3cm}|p{3cm}|p{5cm}|}
	\hline
	\textbf{Type} & \textbf{Color/Format} & \textbf{Use Case} & \textbf{OCR Challenge} \\
	\hline
	\endfirsthead
	\hline
	\textbf{Type} & \textbf{Color/Format} & \textbf{Use Case} & \textbf{OCR Challenge} \\
	\hline
	\endhead
	
	Standard civilian & White bg, black letters, EU blue stripe & Private cars, normal vehicles & Standard OCR, low complexity \\
	
	Electric (E-suffix) & White bg, trailing \texttt{E} & Electric vehicles (EVs) & Detect trailing \texttt{E}, sometimes small font \\
	
	Historic (H-suffix) & White bg, trailing \texttt{H} & Classic/historic cars & Detect \texttt{H} and suffix formatting \\
	
	Green / Tax-exempt & Green bg or markings, black letters & Eco-friendly or certain commercial vehicles & Color recognition + OCR on standard characters \\
	
	Red / Dealer / Export / Temp & Red bg, white letters & Dealership vehicles, export plates, temporary registration & Different font, short-term plates may have non-standard formats \\
	
	Seasonal plates & White bg, month range printed on side & Vehicles registered for specific months & OCR must capture numeric month info \\
	
	Interchangeable / Fleets & White bg, special codes & Business fleet vehicles that move plates between cars & OCR must handle duplicate codes and DB linking \\
	
	Police & Blue/white or special codes & Law enforcement vehicles & Different prefixes, exempt from billing, some use unique reflective paint \\
	
	Fire Brigade / Emergency & Red/white or blue/white & Local fire brigade vehicles & Prefix detection, often short codes \\
	
	Military (Bundeswehr) & White bg, black letters, special prefix & Armed forces & OCR must recognize prefix (e.g., \texttt{Y-12345}) \\
	
	NATO & White bg, NATO code (often Y-...) & NATO military vehicles & Rare patterns, prefix-based recognition \\
	
	Diplomatic & Blue bg (sometimes red), white letters & Embassy/diplomatic corps vehicles & Must detect color + prefix (CD, CC, AT, etc.) \\
	
	Government / State & White bg, special prefix & Federal or state administration & Prefix recognition (e.g., B for Berlin state, other codes for ministries) \\
	
	Consular Corps & Blue/red bg, special codes & Consular staff vehicles & OCR must detect specific prefixes, often color-coded \\
	
	Temporary Import / Transit & Red bg with expiry date & Foreign vehicles temporarily imported & OCR must handle non-standard formatting \\
	
	Old-format plates (pre-1994) & Various, sometimes black-on-white without EU stripe & Rare historic or old cars & OCR may require custom mapping \\
	
	Seasonal Agricultural & Green/white with seasonal suffix & Agricultural vehicles used seasonally & OCR must detect suffix and month numbers \\
	
	Taxi & Yellow/white stripes with T & Commercial taxi vehicles & Color strip detection plus OCR \\
	
	VIP / High-level official & White bg with special prefix & High-ranking officials & Rare format, sometimes exempt from detection \\
	
	Custom / Vanity plates & White bg, custom letters/numbers & Personalized vehicles & OCR must handle non-standard combinations, sometimes creative fonts \\
	
	\hline
\end{longtable}

\section{Challenges and Solutions}
Number Plate Recognition systems deployed in real-world environments face numerous challenges that affect accuracy, robustness, and response time. This section outlines the major challenges encountered during implementation and operation, along with corresponding hardware, software, and operational solutions.

\subsection{Lighting Variations}
\textbf{Effect:} Variations in lighting conditions—such as daytime brightness, night-time darkness, shadowing, or direct glare from headlights—can significantly reduce the reliability of OCR, leading to plate misreads or detection failures. Outdoor installations in parking lots or entry gates are particularly sensitive to these issues \cite{mufti2021automatic, tang2022automatic}. \\  
\textbf{Solution:}
\begin{itemize}
	\item \textbf{Hardware:} Integrate auxiliary LED or infrared (IR) illumination to ensure consistent brightness levels across frames, minimizing overexposure and underexposure \cite{sultan2023applied}.
	\item \textbf{Software:} Employ High Dynamic Range (HDR) imaging, adaptive gamma correction, and histogram equalization to automatically balance exposure and enhance contrast in plate regions \cite{tang2022automatic, tavarez2024comparison}.
	\item \textbf{Operational:} Designate specific stopping zones under uniform lighting and mark these areas clearly to standardize capture conditions for all vehicles.
\end{itemize}

\subsection{Weather Conditions (Rain, Dust, Snow)}
\textbf{Effect:} Environmental conditions such as rain, snow, fog, or dust reduce image clarity, blur plate edges, or obscure characters, leading to OCR and detection errors \cite{plavac2024performance}. Water droplets on camera lenses or reflective snow can further degrade visual quality. \\  
\textbf{Solution:}
\begin{itemize}
	\item Implement multi-frame aggregation to improve recognition confidence under partial occlusions.
	\item Mount cameras at slightly downward angles with weatherproof housings and lens hoods to prevent direct accumulation of moisture or dust.
	\item Use heating or hydrophobic coatings on lenses in areas prone to frost or snow.
	\item Deploy fallback mechanisms such as manual entry or redundant camera views when confidence thresholds fall below acceptable limits.
\end{itemize}

\subsection{Angle and Perspective Distortion}
\textbf{Effect:} License plates captured from extreme angles or height differences appear skewed or distorted, making it difficult for OCR algorithms to correctly identify characters \cite{netinant2024evaluating}. \\  
\textbf{Solution:}
\begin{itemize}
	\item Apply geometric transformation or homography based on plate corner detection to restore rectangular shape.
	\item Encourage proper alignment using ground markings or alignment indicators at checkpoints.
	\item Employ lightweight CNN-based perspective correction modules that learn to normalize skewed inputs in real time.
\end{itemize}

\subsection{Night-time Headlight Glare}
\textbf{Effect:} High-intensity headlights or reflections can saturate camera sensors, causing white patches and obscured text regions \cite{sultan2023applied}. \\  
\textbf{Solution:}
\begin{itemize}
	\item Equip cameras with polarized filters or use near-infrared (NIR) sensors less sensitive to visible light glare.
	\item Capture multiple short-exposure frames and merge them to reconstruct balanced illumination.
	\item Dynamically adjust camera exposure settings and ISO levels based on ambient light detection.
\end{itemize}

\subsection{Dirty, Occluded, or Damaged Plates}
\textbf{Effect:} Dirt, mud, scratches, or stickers can hide parts of the plate, and vehicle tailgating can temporarily obscure the rear plate \cite{mufti2021automatic, sultan2023applied}. \\  
\textbf{Solution:}
\begin{itemize}
	\item Aggregate recognition results across multiple frames to compensate for temporary occlusions.
	\item Use multi-angle camera setups or overhead cameras at critical lanes for redundancy.
	\item Introduce human-in-the-loop verification when automatic detection fails repeatedly.
\end{itemize}

\subsection{Computation and Real-Time Constraints on Edge Devices}
\textbf{Effect:} Edge computing platforms such as the NVIDIA Jetson Nano offer limited processing power. Large deep-learning models can cause dropped frames, reduced frame rates, and latency in decision-making \cite{laroca2018robust, mufti2021automatic}. \\  
\textbf{Solution:}
\begin{itemize}
	\item Adopt a hybrid model approach—using smaller, faster models (e.g., YOLOv8-Nano) for real-time detection and larger models (e.g., YOLOv8-Large) for high-confidence verification.
	\item Apply pruning, quantization, and TensorRT optimizations to reduce model size and accelerate inference \cite{sultan2023applied}.
	\item Implement frame-skipping or adaptive batching strategies to balance speed and accuracy.
\end{itemize}

\subsection{False Positives Due to Background Text}
\textbf{Effect:} Background objects such as advertisements, shop signs, or stickers resembling license plates may trigger false detections \cite{mufti2021automatic}. \\  
\textbf{Solution:}
\begin{itemize}
	\item Restrict plate detection to specific Regions of Interest (ROIs) such as traffic lanes or entry points.
	\item Verify detections by cross-referencing with detected vehicle bounding boxes to ensure spatial consistency.
	\item Apply temporal filtering: accept detections only if the same plate persists across consecutive frames.
\end{itemize}

\subsection{Privacy and GDPR Compliance}
\textbf{Effect:} Since vehicle registration numbers are classified as personal data, improper handling can breach GDPR regulations \cite{mufti2021automatic, sultan2023applied}. \\  
\textbf{Solution:}
\begin{itemize}
	\item Store anonymized or hashed identifiers instead of raw plate numbers.
	\item Encrypt all captured images and enforce automatic data deletion after a defined retention period (e.g., 7–30 days).
	\item Provide visible public notices, maintain access logs, and ensure compliance through periodic audits.
\end{itemize}

\subsection{Tampered or Fake Plates}
\textbf{Effect:} Malicious users may alter or obscure plates using reflective coatings, sprays, or fake fonts, bypassing automated recognition systems \cite{laroca2018robust, mufti2021automatic}. \\  
\textbf{Solution:}
\begin{itemize}
	\item Use rule-based verification against country-specific plate formats to detect anomalies.
	\item Apply anomaly detection algorithms that flag unusual patterns for manual verification.
	\item Integrate database cross-checks with registered vehicle information when legally permitted.
\end{itemize}

\subsection{Environmental and Operational Edge Cases}
\textbf{Effect:} Scenarios such as extreme sunlight angles, dense fog, heavy traffic congestion, or physical obstructions can still degrade detection reliability \cite{plavac2024performance, sultan2023applied}. \\  
\textbf{Solution:}
\begin{itemize}
	\item Combine multiple camera inputs or fuse temporal data to improve robustness.
	\item Schedule routine maintenance such as lens cleaning, angle calibration, and housing inspection.
	\item Continuously monitor performance metrics (e.g., detection confidence) and trigger alerts or model retraining when degradation is observed.
\end{itemize}

\section{System Architecture}
\subsection{Camera Setup}
Single lane, frontal view, 1.5 m height, ROI configured for lane.

\subsection{Inference Pipeline}
\begin{enumerate}
	\item Acquire frame.
	\item YOLOv8-N detection.
	\item Crop candidate plate.
	\item YOLOv8-L validation.
	\item OCR (CRNN/Tesseract/EasyOCR).
	\item Temporal aggregation.
	\item Database update (entry, exit, dwell-time, charge).
\end{enumerate}

\subsection{Database Schema}
The system relies on a **local SQLite database** to track vehicle entries, exits, dwell times, charges, and special plate classifications. This ensures **offline resilience, GDPR compliance**, and auditability.

\begin{table}[h!]
	\centering
	\begin{threeparttable}
		\begin{tabular}{|l|l|p{8cm}|}
			\hline
			\textbf{Field} & \textbf{Data Type} & \textbf{Description} \\
			\hline
			id & INTEGER PRIMARY KEY AUTOINCREMENT & Unique identifier for each vehicle detection event. Ensures all transactions are traceable. \\
			\hline
			plate & TEXT & Detected license plate string. Optionally store hashed version for privacy compliance. \\
			\hline
			plate\_type & TEXT & Classification of plate type: STANDARD, ELECTRIC, HISTORIC, DIPLOMATIC, POLICE, MILITARY, TEMPORARY, EXPORT, etc. Used for billing exemptions and reporting. \\
			\hline
			entry\_ts & DATETIME & ISO 8601 timestamp when the vehicle enters the gate or parking area. \\
			\hline
			exit\_ts & DATETIME & Timestamp when the vehicle exits. Nullable until exit occurs. \\
			\hline
			dwell\_minutes & INTEGER & Calculated dwell time (exit\_ts - entry\_ts) in minutes. Automatically updated on exit. \\
			\hline
			status & TEXT & Workflow status: VALIDATED (detected + OCR successful), MANUAL\_ENTRY (entered by operator), ERROR (failed OCR), EXEMPT (diplomatic, police, military). \\
			\hline
			confidence & FLOAT & Combined YOLOv8 detection confidence and OCR probability. Used to trigger manual verification if below threshold. \\
			\hline
			charge & REAL & Calculated fee in Euro (\texteuro{}) based on dwell time and plate type exemptions. \\
			\hline
			image\_path & TEXT & Optional: path to saved image of the plate capture (encrypted recommended). Useful for auditing or manual verification. \\
			\hline
			notes & TEXT & Free-text field for manual operator remarks, special observations, or system flags. \\
			\hline
		\end{tabular}
		\caption{Expanded local SQL (SQLite) schema for license plate detection and billing system.}
		\label{tab:db_schema}
	\end{threeparttable}
\end{table}

\textbf{Notes:}
\begin{itemize}
	\item \textbf{GDPR Compliance:} Plate numbers can be hashed before storage; images encrypted or retained for limited periods.
	\item \textbf{Operational Use:} The database drives **billing logic**, **manual review triggers**, and **historical reporting**.
	\item \textbf{Scalability:} SQLite is suitable for single-lane or small-to-medium throughput. Multi-lane/high-volume airports should use server-based SQL (PostgreSQL/MySQL) with replication.
\end{itemize}

% ------------------------- BILLING LOGIC -------------------------
\subsection{Billing Logic}
The billing subsystem calculates charges based on **dwell-time** while considering **special exemptions** and **plate categories**. The logic mirrors **typical German airport parking rules** to ensure fairness, transparency, and GDPR compliance.

\subsubsection{Fee Structure}
\begin{itemize}
	\item \textbf{Free Buffer:} 0--10 minutes, accommodates short stop/drop-off scenarios without charge.
	\item \textbf{Incremental Charging:} \texteuro{}2 per 5-minute block after the free buffer. Time rounded up to nearest 5-minute interval.
	\item \textbf{Daily Cap:} Maximum \texteuro{}25 per 24-hour period, consistent with short-term airport parking tariffs.
\end{itemize}

\subsubsection{Exemptions and Special Categories}
Certain vehicles are automatically exempt from charges, detected via **plate type/color/prefix**:
\begin{itemize}
	\item \textbf{Police, Fire Brigade, Emergency Services} -- Exempt, no charges.
	\item \textbf{Diplomatic vehicles and embassy staff} -- Blue/red plates, EXEMPT status.
	\item \textbf{Military/Bundeswehr vehicles} -- Special prefix, EXEMPT.
	\item \textbf{Government / State vehicles} -- Official prefix, EXEMPT.
	\item \textbf{NATO vehicles} -- Rare; EXEMPT.
\end{itemize}

\subsubsection{Plate Classification for Billing}
Charges are determined by plate type detected by OCR and verified in the database. Example mapping:

\begin{table}[h!]
	\centering
	\begin{tabular}{|p{3.5cm}|p{3.5cm}|p{3.5cm}|p{3.5cm}|}
		\hline
		\textbf{Plate Type} & \textbf{Color / Prefix} & \textbf{Billing Category} & \textbf{Notes / Exceptions} \\
		\hline
		Standard civilian & White bg, black letters & Chargeable & Standard incremental billing \\
		\hline
		Electric (E-suffix) & White bg + trailing E & Chargeable & Same as standard; eco-friendly incentives possible \\
		\hline
		Historic (H-suffix) & White bg + H & Chargeable & Some municipalities may reduce fees \\
		\hline
		Red / Dealer / Export / Temp & Red bg & Chargeable / Manual Review & Often temporary; may require operator verification \\
		\hline
		Police & White/blue or special codes & Exempt & No charges; automatic detection critical \\
		\hline
		Diplomatic & Blue/red bg & Exempt & No charges; color + prefix detection required \\
		\hline
		Military (Bundeswehr) & White bg + special prefix & Exempt & Not billed; system flags automatically \\
		\hline
		Government / State & White bg + prefix & Exempt & Official vehicles, no charges \\
		\hline
		NATO & White bg + NATO code & Exempt & Rare; special handling \\
		\hline
		Seasonal plates & White bg + month range & Chargeable & Only charged during active months if calendar-integrated \\
		\hline
	\end{tabular}
	\caption{Billing categories based on German license plate types and exemptions.}
	\label{tab:billing_categories}
\end{table}

\subsubsection{Example Fee Calculation}
\begin{itemize}
	\item \textbf{Case A: Standard civilian car}  
	Entry: 08:05, Exit: 08:50 → Dwell = 45 min  
	Free buffer = 10 min → 35 min chargeable → 7 blocks × \texteuro{}2 = \texteuro{}14
	
	\item \textbf{Case B: Diplomatic car}  
	Entry: 09:10, Exit: 10:30 → Dwell = 80 min  
	Plate recognized as diplomatic → Status = EXEMPT → Fee = \texteuro{}0
	
	\item \textbf{Case C: Electric vehicle}  
	Entry: 14:00, Exit: 15:20 → Dwell = 80 min  
	Free buffer 10 min → 70 min chargeable → 14 blocks × \texteuro{}2 = \texteuro{}28 → Capped at daily max \texteuro{}25
\end{itemize}

\subsubsection{Operational Notes}
\begin{itemize}
	\item Plates failing OCR or classification are flagged for **manual review**.
	\item Exemptions are enforced automatically based on plate type/color/prefix to avoid human error.
	\item The **dwell-time calculation** is linked directly to the **database schema**; timestamps recorded per entry/exit event.
	\item Daily caps ensure long-term parkers do not exceed reasonable airport rates.
\end{itemize}


\section{OCR Methods}
The system evaluates multiple OCR methods suitable for license plate recognition in Germany:

\begin{itemize}
	\item \textbf{Tesseract:} A mature, general-purpose OCR engine. Performs well on high-quality, clean images; supports multilingual text including German characters. May require pre-processing for skewed or low-light plates.
	\item \textbf{CRNN (Convolutional Recurrent Neural Network):} Ideal for sequence modeling on constrained text such as license plates. Provides high accuracy on variable plate formats and suffixes (E, H, diplomatic, etc.).
	\item \textbf{EasyOCR:} Lightweight, supports multiple languages, and suitable for low-latency edge deployment. Handles moderate distortions but less accurate on heavily occluded or dirty plates compared to CRNN.
\end{itemize}

\section{Example Scenarios}
Demonstrative use-cases for system behavior:

\begin{itemize}
	\item \textbf{Normal civilian vehicle:} Plate successfully recognized; dwell-time = 35 minutes → billing calculation: \texteuro{}10. System logs detection confidence and transaction in database.
	\item \textbf{Diplomatic vehicle:} Plate color (blue/red) and prefix detected → system sets status = EXEMPT → fee = \texteuro{}0. Ensures compliance with international and local regulations.
	\item \textbf{Rain/dirty plate:} OCR confidence low due to environmental factors → system triggers **manual entry prompt** or multi-frame aggregation for verification.
	\item \textbf{Electric or historic vehicle:} Suffix E or H detected → system applies specialized billing rules; may trigger eco-friendly discounts or municipality-specific reductions.
	\item \textbf{Temporary / dealer / export plate:} Red-colored plate detected → system flags for manual verification to confirm dwell-time billing.
\end{itemize}

\section{Legal and Privacy Considerations}
Compliance and privacy form a core component of system design:

\begin{itemize}
	\item \textbf{GDPR Compliance:} Minimal data storage, hashed plate numbers, encryption of stored images, defined retention periods.
	\item \textbf{German BDSG Compliance:} Adherence to national data protection law requirements for video and license plate recording.
	\item \textbf{Transparency and Operational Policies:} Proper signage for drivers, clear operator guidelines, access logs, and audit trails to ensure lawful and transparent operations.
	\item \textbf{Automated Exemptions:} Detection of diplomatic, police, and military plates is performed automatically to prevent misuse or human error.
\end{itemize}

\section{Limitations and Future Work}
Despite robustness, the system has some limitations and areas for improvement:

\begin{itemize}
	\item \textbf{Scalability:} Multi-lane or high-throughput scenarios may require multiple synchronized cameras and distributed edge processing.
	\item \textbf{Registry Cross-Checks:} Access to vehicle registries for verification may be restricted by law; alternative verification workflows may be necessary.
	\item \textbf{Environmental Robustness:} Heavy rain, snow, or severe glare can reduce OCR confidence; future work may include adaptive lighting, HDR processing, and adversarial robustness.
	\item \textbf{Integration Opportunities:} Linking with payment systems, airport Fast Tag systems, and centralized parking management platforms for automation and real-time billing.
	\item \textbf{Advanced Analytics:} Collecting anonymized statistics for traffic flow, dwell-time analysis, and predictive parking optimization.
\end{itemize}

\section{Summary}
This chapter establishes a comprehensive foundation for the single-camera YOLOv8 license plate detection and billing system in German airport and secured parking contexts.  
It provides detailed coverage of:

\begin{itemize}
	\item OCR methods and their suitability for diverse German plate types.
	\item Operational example scenarios including exemptions, errors, and billing.
	\item Legal and privacy compliance measures aligned with GDPR and BDSG.
	\item System limitations and future work directions for scalability, robustness, and integration.
\end{itemize}

These foundations ensure a **robust technical, operational, and legal base** for subsequent methodology, implementation, testing, and evaluation chapters.
