%%%
%
% $Autor: Shubhankar Dumka, Gautam Ramesh, Siddhanth Sharma $
% $Date: 2026-01-24 $
% $File: Monitoring.tex $
% $Version: 1.0 $
%
% !TeX spellcheck = en_GB
% !TeX program = pdflatex
% !TeX encoding = utf8
%
%%%

\chapter{\textcolor{red}{Monitoring}}
\label{ch:monitoring}
\index{Monitoring}

\noindent
This chapter documents how the running license plate recognition system is observed, validated, and maintained over time on an edge device (NVIDIA Jetson Nano).
The goal is a realistic, student-project scale approach: lightweight monitoring that fits the compute/storage constraints and works without cloud dependencies.

% --------------------------------------------------------
\section{Idea and Motivation}
\index{Monitoring!Idea and Motivation}

\noindent
Once deployed, the pipeline (camera $\rightarrow$ detection $\rightarrow$ OCR $\rightarrow$ database) can degrade due to environmental changes (lighting, camera angle), hardware limits (thermal throttling), or simple runtime issues (camera disconnects, corrupted frames).
Monitoring is therefore required to (i) detect failures early, (ii) preserve evidence for debugging, and (iii) collect new data for iterative improvement.

\noindent
The core objectives for this project are:
\begin{itemize}
	\item \textbf{Performance:} ensure the system stays responsive (e.g., stable processing rate / acceptable latency).
	\item \textbf{Hardware health:} detect resource pressure and thermal throttling on the Jetson Nano.
	\item \textbf{Availability:} detect crashes, camera failures, and model-load failures quickly.
	\item \textbf{Data quality:} identify unreadable/low-quality plate crops and collect them as new training data.
\end{itemize}

% --------------------------------------------------------
\section{Plan / Description (Implementation Approach)}
\index{Monitoring!Plan / Description}

\subsection{What is monitored}
\index{Monitoring!Plan / Description!What is monitored}

\noindent
The project uses a small set of practical signals that are easy to collect locally:
\begin{itemize}
	\item \textbf{Detection/OCR quality:} plate text, OCR confidence, and whether the output matches a German plate format.
	\item \textbf{Throughput indicator:} processing interval / FPS-style feedback during testing (e.g., camera test scripts overlay FPS).
	\item \textbf{System resources (Jetson):} temperature, CPU/GPU load, memory usage, and disk space using built-in OS tools.
	\item \textbf{Operational events:} errors such as camera not opening, empty frames, and model-load failures.
\end{itemize}

\subsection{How metrics are collected and stored}
\index{Monitoring!Plan / Description!Collection and storage}

\noindent
To remain feasible on a Jetson Nano, metrics are stored locally and kept simple:
\begin{itemize}
	\item \textbf{Event log (SQLite):}
	detections are persisted in a lightweight SQLite database using \PYTHON{sqlite3}.
	In the reference implementation, \PYTHON{DatabaseManager} (see \FILE{Code/LicencePlateDetection/jetson\_app/db.py}) stores \PYTHON{plate\_text}, \PYTHON{confidence}, and \PYTHON{timestamp} in the local database file\linebreak
	\FILE{Code/LicencePlateDetection/jetson\_app/parking.db}.
	\item \textbf{Failure evidence (images):}
	when a plate crop cannot be read, the system stores the crop image in a dedicated directory for later analysis (created on demand in \FILE{Code/LicencePlateDetection/jetson\_app/dashboard.py}).
	\item \textbf{Resource snapshots (manual / scheduled):}
	during testing and demos, Jetson resource metrics can be observed with \SHELL{tegrastats} or by reading thermal sensors from \FILE{/sys/devices/virtual/thermal/}.
	If required, these outputs can be appended to a plain log file at a low frequency (e.g., every 10--30 seconds) to avoid overhead.
\end{itemize}

\subsection{Simple monitoring architecture}
\index{Monitoring!Plan / Description!Architecture}

\noindent
The monitoring concept follows the deployed data flow:
	\begin{enumerate}
		\item \textbf{Camera input} is validated (camera opens, frames are non-empty).
		\item \textbf{Detection} runs with a confidence threshold (example: \PYTHON{conf=0.2} in \FILE{Code/LicencePlateDetection/jetson\_app/detector.py}).
		\item \textbf{OCR pipeline} validates output format and confidence (example: \PYTHON{validateGermanPlate()} and \PYTHON{confThreshold}).
		\item \textbf{Logging layer} writes a minimal event record (SQLite) and stores failure samples as images.
		\item \textbf{Operator checks} (during operation) confirm system resources and review logs/samples.
	\end{enumerate}

% --------------------------------------------------------
\section{Getting New Data During Operation}
\index{Monitoring!Getting New Data}

\noindent
To improve robustness over time, the system collects new samples from real operation instead of relying purely on the original dataset.
The collection strategy is intentionally selective to control storage usage on the edge device.

\subsection{Trigger-based capture}
\index{Monitoring!Getting New Data!Trigger-based capture}

\noindent
New data is captured under conditions that indicate that the current model/pipeline struggles:
\begin{itemize}
	\item \textbf{Unreadable OCR:} if the OCR result is empty or invalid, the best plate crop is stored for later inspection (see \FILE{Code/LicencePlateDetection/jetson\_app/dashboard.py}).
	\item \textbf{High-confidence detections:} the detector script periodically saves frames and plate crops when detection confidence exceeds a threshold (example: \PYTHON{captureConfidence=0.5} with a minimum interval of \PYTHON{1500ms} in \FILE{Code/LicencePlateDetection/jetson\_app/detector.py}).
	\item \textbf{Sharpest sample selection:} multiple candidate crops are buffered and the sharpest crop is selected using the variance of Laplacian (implemented in \FILE{Code/LicencePlateDetection/jetson\_app/dashboard.py}).
\end{itemize}

\noindent
This approach creates a focused "hard cases" dataset (blur, glare, angle issues, partial occlusions) that is valuable for retraining and debugging.

% --------------------------------------------------------
\section{Data Updating in the ML Pipeline}
\index{Monitoring!Data Updating in the ML Pipeline}

\noindent
Retraining in this student project is intentionally \textbf{offline and partially manual}.
The Jetson Nano focuses on inference, while dataset curation and training are performed on a development machine or a controlled environment.

\subsection{Review and annotation workflow}
\index{Monitoring!Data Updating in the ML Pipeline!Review and annotation}

\noindent
The stored captures are periodically reviewed:
\begin{itemize}
	\item Remove corrupted or unusable images (e.g., empty crops).
	\item Label new plates (bounding boxes in YOLO format) and, if required, create corresponding OCR ground truth for evaluation.
	\item Track the data source and conditions (night/day, rain, camera position) as lightweight metadata (directory naming or CSV).
\end{itemize}

\subsection{Retraining and model update}
\index{Monitoring!Data Updating in the ML Pipeline!Retraining and deployment}

\noindent
The model update strategy is:
\begin{enumerate}
	\item Train or fine-tune the detector offline (example script: \FILE{Code/LicencePlateDetection/scripts/train\_german\_lpr.py}).
	\item Validate the new model on a fixed local test set (same image set each iteration) and on recent "hard cases" collected from operation.
	\item Deploy by replacing the model artifact on the Jetson (e.g., updated \PYTHON{best.pt} weights) and re-running the startup checks.
\end{enumerate}

\noindent
Basic versioning is achieved by keeping dated model folders (e.g., \texttt{runs/train/...}) and preserving the previous working model for rollback.

% --------------------------------------------------------
\section{Checks (System Health Validation)}
\index{Monitoring!Checks}

\noindent
Checks are used at three times: \textbf{startup}, \textbf{runtime}, and \textbf{periodic review}.

\subsection{Startup checks}
\index{Monitoring!Checks!Startup}

\begin{itemize}
	\item \textbf{Python environment sanity:} verify imports and camera access using the project script \FILE{report/Code/SystemTools/python\_project\_sanity\_check.py}.
	\item \textbf{Model availability:} verify the expected model file exists before starting inference (paths are printed during initialization in \FILE{Code/LicencePlateDetection/jetson\_app/dashboard.py}).
	\item \textbf{Database readiness:} ensure the SQLite table exists on startup (\PYTHON{DatabaseManager.\_create\_table()} in \FILE{Code/LicencePlateDetection/jetson\_app/db.py}).
\end{itemize}

\subsection{Runtime checks}
\index{Monitoring!Checks!Runtime}

\begin{itemize}
	\item \textbf{Frame validity:} skip empty frames / empty plate crops (handled in\linebreak
	\FILE{Code/LicencePlateDetection/jetson\_app/ocr\_pipeline.py} and\linebreak
	\FILE{Code/LicencePlateDetection/jetson\_app/dashboard.py}).
	\item \textbf{Camera fallback:} attempt an external camera first and fall back to a default camera index if unavailable (implemented in\linebreak
	\FILE{Code/LicencePlateDetection/jetson\_app/dashboard.py}).
	\item \textbf{Output plausibility:} validate plate text against a German plate pattern before accepting it (implemented in\linebreak
	\PYTHON{validateGermanPlate()} in\linebreak
	\FILE{Code/LicencePlateDetection/jetson\_app/ocr\_pipeline.py}).
\end{itemize}

\subsection{Periodic review checks}
\index{Monitoring!Checks!Periodic review}

\noindent
During longer runs or demos, logs and system resources are reviewed:
\begin{itemize}
	\item \textbf{SQLite growth:} ensure the database file does not grow without bounds:\linebreak
	\FILE{Code/LicencePlateDetection/jetson\_app/parking.db}.
	\item \textbf{Disk usage:} ensure the capture directories do not fill the device storage.
	\item \textbf{Thermals:} check for thermal throttling symptoms (e.g., sudden FPS drops) and verify with Jetson OS tools.
\end{itemize}

% --------------------------------------------------------
\section{Code: Monitoring-Related Functions}
\index{Monitoring!Code Functions}

\noindent
To keep monitoring logic maintainable, the project separates core concerns into small functions/classes:
\begin{itemize}
	\item \textbf{Event persistence:} \PYTHON{DatabaseManager.log\_detection()} and \PYTHON{get\_first\_detection\_today()} in \FILE{Code/LicencePlateDetection/jetson\_app/db.py} encapsulate SQLite operations.
	\item \textbf{Quality gating:} \PYTHON{PlateOcrPipeline.readPlate()} combines preprocessing, OCR execution, normalization, and format validation in one reusable pipeline (\FILE{Code/LicencePlateDetection/jetson\_app/ocr\_pipeline.py}).
	\item \textbf{Sample selection:} sharpness scoring and buffering reduce noisy captures and improve the quality of stored samples (\FILE{Code/LicencePlateDetection/jetson\_app/dashboard.py}).
	\item \textbf{Performance feedback (testing):} \PYTHON{draw\_fps()} in \FILE{Code/LicencePlateDetection/scripts/test\_camera.py} provides quick runtime feedback during development.
\end{itemize}

% --------------------------------------------------------
\section{Code: Test Strategy}
\index{Monitoring!Code Test}

\noindent
Testing focuses on fast checks that catch deployment blockers early:
\begin{itemize}
	\item \textbf{Import and environment tests:} validate dependencies and basic runtime readiness (example: \FILE{Code/LicencePlateDetection/scripts/test\_yolo\_import.py} and \FILE{report/Code/SystemTools/python\_project\_sanity\_check.py}).
	\item \textbf{Camera and throughput tests:} validate camera read loop and visual overlays (example: \FILE{Code/LicencePlateDetection/scripts/test\_camera.py}).
	\item \textbf{End-to-end dry runs:} run the full pipeline and confirm that detections appear in SQLite and that unreadable crops are stored when OCR fails (dashboard run).
\end{itemize}

% --------------------------------------------------------
\section{Privacy}
\index{Monitoring!Privacy}

\noindent
License plates are personal data in many jurisdictions, therefore monitoring must minimize data exposure:
\begin{itemize}
	\item \textbf{Data minimization:} the default operational log stores plate text, timestamp, and confidence (SQLite) instead of storing full video streams.
	\item \textbf{Restricted access:} logs and captured images remain on the device and are intended for project team access only.
	\item \textbf{Retention:} captured images for debugging/retraining should be deleted after they have been reviewed and incorporated into an updated dataset; database entries should be pruned to a defined retention window (e.g., last N days) for the demo setup.
\end{itemize}

% --------------------------------------------------------
\section{Robustness}
\index{Monitoring!Robustness}

\noindent
The system is designed to degrade gracefully under common edge failures:
\begin{itemize}
	\item \textbf{Camera issues:} the application detects missing cameras and either falls back to another device index or terminates with a clear error.
	\item \textbf{OCR failures:} empty/invalid crops are handled without crashing, and failures are recorded as samples for later improvement.
	\item \textbf{GPU/CPU variability:} OCR can run on CPU if GPU resources are constrained (fallback behaviour exists in \PYTHON{PlateOcrPipeline.\_ensureReader()} in \FILE{Code/LicencePlateDetection/jetson\_app/ocr\_pipeline.py}).
\end{itemize}

% --------------------------------------------------------
\section{Process (Operational Workflow)}
\index{Monitoring!Process}

\noindent
A typical operational workflow for a demo run on the Jetson Nano is:
\begin{enumerate}
	\item \textbf{Start:} run the sanity check (\FILE{report/Code/SystemTools/python\_project\_sanity\_check.py}), then start the dashboard application.
	\item \textbf{Observe:} verify that the UI updates, detections are shown, and that \FILE{Code/LicencePlateDetection/jetson\_app/parking.db} records events.
	\item \textbf{Monitor resources:} periodically check Jetson temperatures and utilization using OS tools during longer runs.
	\item \textbf{Stop:} terminate the application cleanly and archive logs/captures if needed.
	\item \textbf{Review:} inspect unreadable/failed captures and add useful samples to the retraining dataset.
\end{enumerate}

\noindent
Example decision rules used during operation:
\begin{itemize}
	\item If the processing rate drops noticeably, check Jetson thermals and system load; reduce camera resolution or processing frequency if necessary.
	\item If many plates become unreadable, inspect recent captures to identify whether the cause is motion blur, lighting changes, or camera focus, and collect samples for retraining.
	\item If detections are missing entirely, run the startup checks again (camera access, model path, CUDA availability) before changing thresholds.
\end{itemize}
