%%%
%
% $Autor: Wings $
% $Datum: 2021-05-14 $
% $Pfad:  $
% $Dateiname: SBOM
% $Version: 4620 $
%
% !TeX spellcheck = de_DE/GB
% !TeX program = pdflatex
% !BIB program = biber/bibtex
% !TeX encoding = utf8
%
%%%

\chapter{\textcolor{red}{SBOM}}
\setlength{\tabcolsep}{6pt} % horizontal padding
\setlength{\extrarowheight}{2pt} % vertical padding

\vspace{0.5cm} % top margin

\begin{center}
	\begin{longtable}{|p{2cm}|p{2.5cm}|p{2cm}|p{4.2cm}|p{2.3cm}|}
		\hline
		\textbf{Category} & \textbf{Software / Library} & \textbf{Version / Platform} & \textbf{Purpose / Usage} & \textbf{License / Type} \\
		\hline
		\endfirsthead
		
		\hline
		\textbf{Category} & \textbf{Software / Library} & \textbf{Version / Platform} & \textbf{Purpose / Usage} & \textbf{License / Type} \\
		\hline
		\endhead
		
		\hline
		\multicolumn{5}{r}{\textit{Continued on next page}} \\
		\endfoot
		
		\hline
		\endlastfoot
		
		Operating System & NVIDIA JetPack SDK 5.1.2 (Ubuntu 20.04 LTS) & Jetson Nano (ARM64) & Provides Ubuntu base OS with CUDA, cuDNN, TensorRT, and OpenCV preinstalled. & Mixed — Ubuntu is \textit{Open Source (GPL)}; NVIDIA JetPack components are \textit{Free (proprietary binaries)} \\
		\hline
		Programming Language & Python 3.11 & Installed via \texttt{sudo apt install python3} & Primary development language for the ML pipeline. & Open Source (PSF License) \\
		\hline
		Machine Learning Framework & PyTorch + TorchVision & Jetson-compatible build (PyTorch 2.x) & Runs YOLOv8 models for object detection. & Open Source (BSD-style) \\
		\hline
		Object Detection Model & YOLOv8-n / YOLOv8-s (Ultralytics) & Installed via \texttt{pip install ultralytics} & Real-time license plate detection. & Free tier, \textit{AGPLv3} (open-source use); commercial license available \\
		\hline
		OCR Engine & EasyOCR / PaddleOCR & EasyOCR 1.7.0+ & Recognizes alphanumeric text from detected license plates. & Open Source (Apache 2.0 / MIT) \\
		\hline
		Computer Vision Toolkit & OpenCV & 4.5+ & Image capture, preprocessing, and bounding box drawing. & Open Source (Apache 2.0) \\
		\hline
		Database & SQLite3 (Python library) & Built-in & Local storage for detected plate numbers and logs. & Public Domain (Open Source) \\
		\hline
		Data Analysis \& Visualization & Pandas, NumPy, Matplotlib & Latest & Data logging, performance evaluation, and visualization. & Open Source (BSD / MIT) \\
		\hline
		Deployment \& Automation & systemd / crontab (Linux) & Built-in & Automates script startup and scheduling. & Open Source (GPL / LGPL) \\
		\hline
		Package Management & PIP \& APT & Latest & Manages Python and system dependencies. & Open Source (MIT / GPL) \\
		\hline
		IDE / Code Editor & Visual Studio Code & Desktop / SSH & Code development and debugging. & Proprietary (Free Tier under Microsoft License) \\
		\hline
		Version Control & Git \& GitHub & Latest & Source control, versioning, and collaboration. & Git: \textit{Open Source (GPLv2)}; GitHub: \textit{Proprietary (Free Tier Available)} \\
		\hline
		Model Optimization & TensorRT (JetPack component) & Built-in & Optimizes YOLOv8 model for faster inference on Jetson. & Free, Proprietary (NVIDIA License) \\
		\hline
		Testing \& Debugging Tools & Jupyter Notebook & Python package & Interactive model testing and visualization. & Open Source (BSD License) \\
		\hline
		Dataset Annotation Tool & LabelImg / Roboflow & Latest & Labeling license plate bounding boxes for training. & LabelImg: \textit{Open Source (MIT)}; Roboflow: \textit{Proprietary (Free Tier Available)} \\
		\hline
		\caption{Software stack for license plate detection on Jetson Nano.} % caption at the bottom
	\end{longtable}
\end{center}

\vspace{0.5cm} % bottom margin


\FILE{requirements.txt}
