%%%%%%%%%%%%
%
% $Autor: Wings $
% $Datum: 2019-03-05 08:03:15Z $
% $Pfad: Troubleshooting.tex $
% $Version: 4250 $
% !TeX spellcheck = en_GB/de_DE
% !TeX encoding = utf8
% !TeX root = manual 
% !TeX TXS-program:bibliography = txs:///biber
%
%%%%%%%%%%%%

\chapter{Frequently Asked Questions (FAQ)}

This chapter addresses common questions about the Vehicle License Plate Detection System, offering quick answers and solutions.

\section{General Questions}
\begin{itemize}[label=--, left=1.5em]
	\item \textbf{Q: What camera models are compatible with the Jetson Nano J1010?}  
	A: The system generally supports CSI cameras compatible with the Jetson Nano, as well as USB cameras. Check the NVIDIA documentation for a full list of compatible models.
	
	\item \textbf{Q: Can I use the system with a Wi-Fi connection?}  
	A: Yes, the system can connect to Wi-Fi using a compatible USB Wi-Fi adapter, enabling remote operation and updates.
\end{itemize}

\section{Setup and Configuration}
\begin{itemize}[label=--, left=1.5em]
	\item \textbf{Q: Why is my camera not detected by the system?}  
	A: Ensure the camera is securely connected to the Jetson Nano, and verify that the necessary drivers are installed. Restart the system if needed.
	
	\item \textbf{Q: How can I adjust the detection accuracy of the model?}  
	A: Improve accuracy by training the model with a larger dataset or adjusting camera settings to ensure clear images.
\end{itemize}

\section{Performance and Operation}
\begin{itemize}[label=--, left=1.5em]
	\item \textbf{Q: Why is the detection system running slower than expected?}  
	A: Slow performance can result from insufficient power or high ambient temperatures. Ensure adequate cooling and try using the maximum performance mode on the Jetson Nano.
	
	\item \textbf{Q: How do I reduce false detections?}  
	A: False detections can be minimized by fine-tuning model thresholds, improving lighting conditions, and using a more refined training dataset.
\end{itemize}

\section{Maintenance and Troubleshooting}
\begin{itemize}[label=--, left=1.5em]
	\item \textbf{Q: How often should I update the software?}  
	A: Regular updates are recommended, especially for JetPack SDK and Python packages, to benefit from new features and fixes.
	
	\item \textbf{Q: What should I do if the system stops responding?}  
	A: Restart the Jetson Nano by powering it off and on. If the issue persists, check all connections and power sources.
\end{itemize}

For further assistance, consult the official NVIDIA Jetson documentation or reach out to support forums for more specific guidance.



