%%%%%%%%%%%%%%%%%%%%%%%%
%
% $Autor: Gautam Ramesh$
% $Datum: 2025-10-14 21:49:26Z $
% $Pfad: /Users/gautamramesh/githubNew/ML26-03-Car-Licence-Plate-Identification-with-a-Jetson-Nano/Assembly - edit/Chapters/en/Maintenance.tex $
% $Version: 1 $
%
% !TeX encoding = utf8
% !TeX root = Rename
%
%%%%%%%%%%%%%%%%%%%%%%%%



\chapter{Maintenance and Preventive Care}

Regular maintenance ensures long-term stability, performance, and safety of the Jetson Nano-based License Plate Detection System.  
This section provides practical instructions for cleaning, inspecting, updating, and servicing the hardware to maximize uptime and lifespan.

% -------------------------------------------------------
\section{General Maintenance Guidelines}

\begin{itemize}
	\item \textbf{Power Off Before Service:} Always shut down the Jetson Nano safely using the desktop interface or \texttt{sudo poweroff} before disconnecting cables.
	\item \textbf{Avoid Static Damage:} Ground yourself before touching GPIO or USB ports to prevent electrostatic discharge (ESD).
	\item \textbf{Cable Management:} Ensure cables are untangled and securely seated; label connections for quick reference.
	\item \textbf{Physical Cleanliness:} Remove dust buildup on heatsinks, fans, and camera lens every month using compressed air or a soft brush.
	\item \textbf{Environmental Control:} Maintain ambient temperatures between \SI{10}{\celsius}–\SI{35}{\celsius}; avoid high humidity or enclosed spaces without ventilation.
\end{itemize}

\vspace{0.5cm}

% -------------------------------------------------------
\section{Periodic Maintenance Schedule}

\begin{table}[H]
	\centering
	\caption{Recommended Maintenance Schedule}
	\begin{tabular}{|L{3.2cm}|L{7.8cm}|L{3.0cm}|}
		\hline
		\textbf{Component} & \textbf{Task} & \textbf{Frequency} \\ \hline
		Jetson Nano Board & Inspect GPIO pins, connectors, and heatsink; verify SD card slot alignment & Monthly \\ \hline
		Cooling System (Fan / Heatsink) & Clean dust and test fan rotation; check noise levels & Every 2 months \\ \hline
		USB Camera & Wipe lens gently with microfiber; test frame rate and focus accuracy & Monthly \\ \hline
		Power Adapter / Barrel Jack & Ensure 5V/4A output with multimeter; inspect for loose connectors & Every 3 months \\ \hline
		HDMI and USB Cables & Test connectivity and cable integrity; replace if frayed or loose & Every 3 months \\ \hline
		microSD Card & Backup and clone working OS image; check filesystem integrity & Quarterly \\ \hline
	\end{tabular}
\end{table}

\vspace{0.4cm}

Routine adherence to this schedule minimizes failures caused by overheating, dust accumulation, or storage corruption.

% -------------------------------------------------------
\section{Software and System Maintenance}

\begin{itemize}
	\item \textbf{System Updates:} Keep JetPack and Ubuntu packages updated using:
	\begin{verbatim}
		sudo apt update && sudo apt upgrade -y
	\end{verbatim}
	
	\item \textbf{Backup Configuration:} Regularly copy the following folders:
	\begin{itemize}
		\item \texttt{/home/jetson/ANPR/} – Source code and models
		\item \texttt{/etc/network/interfaces} – Network settings
		\item \texttt{/var/log/} – Operation logs for debugging
	\end{itemize}
	
	\item \textbf{Model Refresh:} Retrain YOLOv8 or EasyOCR models every 6–12 months if license plate formats or fonts change.
	\item \textbf{Database Optimization:} Vacuum and clean the SQLite database periodically:
	\begin{verbatim}
		sqlite3 plates.db "VACUUM;"
	\end{verbatim}
	\item \textbf{Swap File Check:} Ensure swap memory is active for stable inference on long runs:
	\begin{verbatim}
		free -h
	\end{verbatim}
\end{itemize}

% -------------------------------------------------------
\section{Visual Maintenance Overview}

\begin{figure}[H]
	\centering
	\begin{tikzpicture}[
		every node/.style={font=\scriptsize, align=center},
		comp/.style={draw, rounded corners=3pt, fill=blue!10, minimum width=2.8cm, minimum height=1.0cm},
		task/.style={draw, rounded corners=3pt, fill=orange!10, minimum width=3.2cm, minimum height=1.0cm},
		arr/.style={-{Latex[length=2mm]}, thick}
		]
		\node[comp] (nano) {Jetson Nano\\(Board)};
		\node[task, above left=1.2cm and 2.4cm of nano] (clean) {Clean Heatsink / Fan};
		\node[task, above=1.2cm of nano] (update) {Run Software Updates};
		\node[task, above right=1.2cm and 2.4cm of nano] (backup) {Backup SD / Logs};
		
		\node[comp, below left=1.2cm and 2.4cm of nano] (camera) {USB Camera};
		\node[comp, below=1.2cm of nano] (psu) {Power Adapter};
		\node[comp, below right=1.2cm and 2.4cm of nano] (display) {HDMI Display};
		
		\draw[arr] (clean.south) -- (nano.north west);
		\draw[arr] (update.south) -- (nano.north);
		\draw[arr] (backup.south) -- (nano.north east);
		\draw[arr] (camera.north) -- (nano.south west);
		\draw[arr] (psu.north) -- (nano.south);
		\draw[arr] (display.north) -- (nano.south east);
	\end{tikzpicture}
	\caption{Maintenance overview: routine checks for board, peripherals, power, and software updates.}
\end{figure}

% -------------------------------------------------------
\section{Backup and Replacement Procedure}

\begin{enumerate}
	\item Clone the working microSD card using \texttt{balenaEtcher} or \texttt{dd} to create a fallback image.
	\item Label the cloned card clearly.
	\item Store backup images on a separate USB drive or network share.
	\item Replace damaged components with same-rated parts only (e.g., \SI{5}{\volt}/\SI{4}{\ampere} adapter).
	\item Document every replacement or major update in a maintenance log file.
\end{enumerate}

% -------------------------------------------------------
\section{Safety and Warranty Considerations}

\begin{itemize}
	\item Avoid modifying the mainboard or GPIO layout without referencing the official NVIDIA Jetson Nano Developer Kit manual.
	\item Using non-certified power supplies may void warranty or damage the board.
	\item Handle peripherals gently; avoid connecting or disconnecting under power.
	\item Follow ESD safety practices while handling camera or GPIO accessories.
\end{itemize}

\vspace{0.6cm}
\noindent
