%%%
%
% $Autor: Wings $
% $Datum: 2021-05-14 $
% $Pfad: GitLab/CornerBLending $
% $Dateiname: Hints
% $Version: 4620 $
%
% !TeX spellcheck = de_DE/GB
%
%%%



\chapter{Getting Started}

\begin{tcolorbox}[
	enhanced,
	colback=blue!3!white,
	colframe=blue!70!black,
	coltitle=black,
	title={\faRocket\hspace{0.5em}\textbf{Welcome to the Smart License Plate Detection System}},
	fonttitle=\bfseries\large,
	left=8pt,
	right=8pt,
	top=8pt,
	bottom=8pt,
	boxrule=1pt,
	rounded corners,
	shadow={1mm}{-1mm}{0.3mm}{black!40}, % ✅ fixed units (mm not pt)
	borderline={0.5pt}{0pt}{blue!40!black,dashed},
	before skip=8pt,
	after skip=12pt,
	breakable
	]
	
	\noindent
	\textbf{Dear User,}\\[4pt]
	Welcome to your \textbf{Smart License Plate Detection System} — a reliable ML-powered solution developed at \textbf{Hochschule Emden–Leer}.  
	This device uses advanced edge computing on the \textbf{NVIDIA Jetson Nano} to automatically recognise and log vehicle license plates in real time.
	
	\vspace{0.6em}
	\hspace{0.3em}The system starts automatically when powered on — no setup or configuration is required.  
	Within seconds, it begins detecting and displaying vehicles on screen with accurate entry, exit, and duration details.
	
	\vspace{0.6em}
	\faCogs\hspace{0.3em}\textbf{Key Highlights:}
	\begin{itemize}
		\item Works entirely offline — no internet required.
		\item Designed for 24/7 airport gate operation.
		\item Automatically handles billing for stays beyond 15 minutes.
		\item Recognises exempt vehicles (police, ambulance, government).
		\item Compact, efficient, and easy to maintain.
	\end{itemize}
	
	
	\vspace{0.8em}
	\begin{center}
		\textit{"Technology that simplifies — accuracy that empowers."}\\[6pt]
		\small Developed by \textbf{Gautam Ramesh}, \textbf{Siddhanth Sharma}, and \textbf{Shubhankar Dumka}\\[3pt]
		\texttt{gautam.ramesh.1@stud-hs-emden-leer.de}\\
		\texttt{siddhanth.sharma@stud.hs-emden-leer.de}\\
		\texttt{shubhankar.dumka@stud.hs-emden-leer.de}
	\end{center}
	
\end{tcolorbox}

% --------------------------------------------------
% Section 1: Quick Pre-Start Hints
% --------------------------------------------------
\section*{Before You Start}

\begin{itemize}
	\item Place the device on a stable, flat surface with good ventilation.
	\item Make sure the \textbf{power supply (5 V / 4 A)} is connected firmly and the cable is not loose.
	\item Keep the \textbf{camera lens clean} for accurate plate reading.
	\item Do not block the openings on the aluminum case; it keeps the system cool.
	\item Avoid exposing the device to rain, moisture, or direct sunlight.
	\item Connect the HDMI cable to your monitor before switching on the power.
	\item Wait until the indicator light turns on — this means the system is ready.
	\item If the display stays blank, check power and camera connections first.
\end{itemize}

\vspace{0.5em}
\noindent
These simple steps help ensure your system starts safely and performs reliably every time.

\vspace{0.8cm}

\begin{tcolorbox}[
	colback=yellow!10,
	colframe=yellow!50!black,
	title={Important to Know Before Use},
	fonttitle=\bfseries,
	left=6pt,
	right=6pt,
	top=6pt,
	bottom=6pt,
	boxrule=0.8pt
	]
	\begin{itemize}
		\item This system records number plates for time tracking and billing at the airport gate.
		\item Do not move or touch the camera once it is aligned. Misalignment can cause unreadable plates.
		\item If a plate is too dirty or not readable, you may need to type it in manually later.
		\item Emergency and official vehicles (police, ambulance, etc.) are recognised as \textbf{no charge}.
		\item Turn off the system only after normal shutdown. Unplugging power while it is running can cause data loss.
	\end{itemize}
\end{tcolorbox}

\vspace{0.6cm}
\noindent
\textit{For detailed instructions on setup and use, please refer to \autoref{ch:system_setup}.}

\vspace{0.5em}
\noindent
These simple steps help ensure your system starts safely and performs reliably every time.

