%%%%%%%%%%%%
%
% $Autor: Wings $
% $Datum: 2019-03-05 08:03:15Z $
% $Pfad: SetUp.tex $
% $Version: 4250 $
% !TeX spellcheck = en_GB/de_DE
% !TeX encoding = utf8
% !TeX root = manual 
% !TeX TXS-program:bibliography = txs:///biber
%
%%%%%%%%%%%%

\chapter{Installation and Set Up}

\section{Required Components}
To set up your Jetson Nano J1010, you will need:
\begin{itemize}[label=--,left=1.5em]
	\item NVIDIA Jetson Nano J1010 board
	\item MicroSD card (16GB or larger) with pre-installed JetPack SDK
	\item USB keyboard and mouse
	\item HDMI monitor
	\item 5V power supply (4A recommended for maximum performance)
\end{itemize}

\section{Installing the Operating System}
\begin{enumerate}
	\item Download the JetPack SDK from \href{https://developer.nvidia.com/embedded/jetpack}{NVIDIA JetPack SDK}.
	\item Flash the image to a MicroSD card using tools like Etcher.
	\item Insert the MicroSD card into the slot on the Jetson Nano J1010.
	\item Connect the HDMI monitor, keyboard, and mouse.
	\item Power on the device by connecting the 5V power supply.
\end{enumerate}

\section{Ethernet Configuration}
\begin{itemize}[label=--,left=1.5em]
	\item Connect a standard Ethernet cable to the Gigabit Ethernet port.
	\item By default, the system will acquire an IP address via DHCP. To set a static IP, modify the \texttt{/etc/network/interfaces} file.
\end{itemize}

\section{Wi-Fi Setup (Optional)}
\begin{enumerate}
	\item Plug in a USB Wi-Fi adapter compatible with Jetson Nano.
	\item Run the following commands to install the necessary packages:
	\begin{verbatim}
		sudo apt-get update
		sudo apt-get install network-manager
	\end{verbatim}
	\item Configure Wi-Fi using the Network Manager GUI or by modifying \texttt{/etc/network/interfaces}.
\end{enumerate}