%%%%%%%%%%%%
%
% $Autor: Wings $
% $Datum: 2019-03-05 08:03:15Z $
% $Pfad: ListOfParts.tex $
% $Version: 4250 $
% !TeX spellcheck = en_GB/de_DE
% !TeX encoding = utf8
% !TeX root = manual 
% !TeX TXS-program:bibliography = txs:///biber
%
%%%%%%%%%%%%

\chapter{List Of Parts}

\section{List of Parts}

This section provides a detailed overview of all hardware components used in the \textbf{License Plate Detection System}.  
Each part listed below was selected for compatibility, durability, and seamless operation with the NVIDIA Jetson Nano edge AI platform.  
All items are off-the-shelf components, easily replaceable or upgradable for future iterations of the system.

\vspace{0.5cm}

\begin{table}[h!]
	\centering
	\caption{List of Materials  – Jetson Nano License Plate Detection System}
	\label{tab:listofparts}
	\renewcommand{\arraystretch}{1.3}
	\begin{tabular}{|p{3.1cm}|p{6.3cm}|p{3.1cm}|p{1.8cm}|}
		\hline
		\textbf{Part Name} & \textbf{Description / Specification} & \textbf{Manufacturer / Model} & \textbf{Quantity} \\
		\hline
		\textbf{Main Processing Unit} & NVIDIA Jetson Nano 4GB Developer Kit with passive heatsink, integrated into Seeed Studio reComputer J1010 aluminum enclosure & Seeed Studio / NVIDIA & 1 \\
		\hline
		\textbf{Camera} & USB 2.0 HD camera for live video capture (2.0 MP resolution), used for license plate detection and OCR input & Microsoft LifeCam Show (Model 1139) & 1 \\
		\hline
		\textbf{Camera Mounting Rod / Stand} & Vertical metallic rod with adjustable clamp base for stable camera positioning and angle alignment (approx. 35–40 cm height) & Generic Steel Stand / Custom Mount & 1 \\
		\hline
		\textbf{Power Supply} & 5V / 4A regulated adapter with USB-C connector & Seeed Studio (or certified equivalent) & 1 \\
		\hline
		\textbf{Storage} & 64 GB microSD card (Class 10 or UHS-I) preloaded with JetPack 5.1.2 (Ubuntu 20.04) & SanDisk / Samsung Evo+ & 1 \\
		\hline
		\textbf{Display} & HDMI display for real-time output visualization (minimum 1080p resolution) & Generic HDMI Monitor / 15.6-inch & 1 \\
		\hline
		\textbf{Networking Cable (Optional)} & Gigabit Ethernet cable for direct connection or remote control access & Cat 6 / 1.5 m length & 1 \\
		\hline
		\textbf{Casing and Mount} & Aluminum reComputer J1010 case with passive heat sink and rubber base for vibration damping & Seeed Studio & 1 \\
		\hline
		\textbf{Peripherals (Optional)} & Wireless keyboard and mouse for setup and debugging & Logitech MK220 (or equivalent) & 1 set \\
		\hline
		\textbf{Software Frameworks} & YOLOv8 (object detection), EasyOCR (text extraction), SQLite (logging), OpenCV (image processing) & Open Source / Python 3.8 Environment & -- \\
		\hline
	\end{tabular}
\end{table}

\vspace{0.4cm}
\noindent
The \textbf{Microsoft LifeCam Show} is mounted on a stable \textbf{vertical metallic stand} that allows flexible height and tilt adjustment to ensure optimal plate visibility during image capture.  
This setup helps maintain consistent camera alignment and minimizes vibration or misfocus during real-time detection.

\vspace{0.3cm}
\noindent
The \textbf{Jetson Nano} acts as the central processing hub, receiving the camera feed via USB, performing YOLOv8 inference, extracting text through EasyOCR, and logging results into an SQLite database.  
All components are designed for compact, plug-and-play integration, with power delivered through a single 5V/4A USB-C supply.

\vspace{0.3cm}
\noindent
For scalability, additional cameras can be connected through the available USB ports or via a powered USB hub, enabling multi-angle detection or extended lane monitoring for advanced future deployments.

\vspace{0.3cm}
\noindent
The system’s modular structure simplifies both \textbf{maintenance and portability}.  
Each module—camera, Jetson Nano, or display—can be detached and reassembled within minutes, enabling quick field deployment or hardware replacement.  
The aluminum enclosure further enhances protection against dust and minor impacts during transportation.

\vspace{0.3cm}
\noindent
The design also emphasizes \textbf{energy efficiency and operational reliability}.  
With an average power consumption of under 10 W, the entire setup can run continuously using a portable power bank or vehicle adapter.  
This makes the system suitable for both indoor and outdoor use cases, such as temporary checkpoints or parking-lot trials.