\definecolor{corpBlue}{RGB}{0, 85, 150}      % Deep Engineering Blue
\definecolor{corpLight}{RGB}{240, 245, 255}  % Very Light Blue Background
\definecolor{accentGray}{RGB}{80, 80, 80}    % Dark Text
\chapter{Maintenance}

\section{Maintenance}

Regular maintenance keeps the \textbf{License Plate Detection System} running smoothly and extends its lifetime.  
This section describes how users can care for the hardware and software to ensure reliable daily operation at the airport gate.

\begin{tcolorbox}[colback=blue!5!white,colframe=blue!60!black,
	title={\hspace{0.5em}Important}, fonttitle=\bfseries]
	\begin{itemize}
		\item Turn off power before cleaning or adjusting cables.  
		\item Avoid using sharp objects or sprays near the camera lens.  
		\item Do not block the ventilation openings of the main unit's case.  
		\item If the device overheats or smells unusual, disconnect power immediately and contact support.
	\end{itemize}
\end{tcolorbox}


% ==========================================================
\subsection{Hardware Maintenance}

\begin{itemize}
	\item \textbf{Keep it clean:}  
	Gently wipe the main unit and camera with a dry microfiber cloth.  
	Avoid liquids, direct sunlight, or dust build-up around the device.
	
	\item \textbf{Check connections:}  
	Ensure all USB, HDMI, and power cables are firmly attached.  
	Loose connections can cause flickering displays or camera interruptions.
	
	\item \textbf{Maintain good cooling:}  
	Place the main unit  in a ventilated area.  
	If the device feels unusually hot, turn it off for a few minutes or use a small desk fan.
	
	\item \textbf{Power stability:}  
	Always use the original 5V/4A USB-C power adapter.  
	Unstable power may lead to sudden restarts or data loss.
	
	\item \textbf{Camera alignment:}  
	Check every few weeks that the camera faces the correct lane and captures clear plates without obstruction.
\end{itemize}

\begin{tikzpicture}[
	font=\sffamily,
	% 1. STYLE: The Central Hub
	hub/.style={
		circle,
		minimum size=3.5cm,
		align=center,
		top color=corpBlue!10,
		bottom color=corpBlue!30,
		draw=corpBlue,
		very thick,
		blur shadow={shadow blur steps=5}
	},
	% 2. STYLE: The Satellite Nodes (Tasks)
	task/.style={
		rectangle,
		rounded corners=5pt,
		minimum width=4cm,
		minimum height=1.2cm,
		align=center,
		fill=white,
		draw=accentGray!30,
		thick,
		blur shadow,
		font=\bfseries\small
	},
	% 3. STYLE: The Connecting Arcs
	cycleArrow/.style={
		-{Latex[width=3mm, length=3mm]},
		line width=1mm,
		draw=corpBlue!80,
		shorten >=5pt,
		shorten <=5pt
	}
	]
	
	% --- CENTRAL HUB ---
	\node[hub] (center) at (0,0) {\textbf{Routine}\\ \textbf{Maintenance}\\ \textbf{Protocol}};
	
	% --- NODES (Polar Coordinates) ---
	% 1. Top Right (45 deg)
	\node[task, anchor=south west] (node1) at (45:2.5cm) {1. OPTICS\\ \normalfont Clean Camera Lens};
	
	% 2. Bottom Right (-45 deg)
	\node[task, anchor=north west] (node2) at (-45:2.5cm) {2. CONNECTIVITY\\ \normalfont Check USB \& Power};
	
	% 3. Bottom Left (-135 deg)
	\node[task, anchor=north east] (node3) at (-135:2.5cm) {3. THERMAL\\ \normalfont Verify Cooling/Fan};
	
	% 4. Top Left (135 deg)
	\node[task, anchor=south east] (node4) at (135:2.5cm) {4. CALIBRATION\\ \normalfont Verify Angle/Focus};
	
	% --- CONNECTING ARROWS (The Cycle) ---
	% Drawing curved arrows between the quadrants
	\draw[cycleArrow] (50:2cm) arc (50:-40:2cm);
	\draw[cycleArrow] (-40:2cm) arc (-40:-130:2cm);
	\draw[cycleArrow] (-130:2cm) arc (-130:-220:2cm);
	\draw[cycleArrow] (140:2cm) arc (140:50:2cm);
	
	% --- DECORATIVE CONNECTORS ---
	% Thin lines connecting center to nodes
	\foreach \angle in {45, -45, -135, 135} {
		\draw[dashed, gray] (0,0) -- (\angle:2.3cm);
		\fill[corpBlue] (\angle:2.3cm) circle (2pt);
	}
	
\end{tikzpicture}

% ==========================================================
\subsection{Software Maintenance}

\begin{itemize}
	\item \textbf{Regular check-ups:}  
	Restart the main unit  once every few days to clear memory and refresh processes.
	
	\item \textbf{Keep the main unit updated:}  
	If an update notification appears, allow the main unit to install recommended main unit updates.
	
	\item \textbf{Database management:}  
	Every few weeks, check that the detection log is not full.  
	If storage is low, export or delete older records safely.
	
	\item \textbf{Model refresh (for developers):}  
	Advanced users can retrain or update the detection model to improve recognition accuracy over time.
\end{itemize}

% --- To-Do image placeholder: software update screen ---


% ==========================================================
\subsection{Backup and Safety}

\begin{itemize}
	\item \textbf{Weekly backup:}  
	Copy the database file (\texttt{plates.db}) to a USB drive or computer for safekeeping.
	
	\item \textbf{Power off correctly:}  
	Always shut down the device through the desktop before unplugging power.
	
	\item \textbf{Avoid sudden shutdowns:}  
	Interrupting the main unit during detection can damage stored data.
	
	\item \textbf{Emergency reset:}  
	If the screen freezes, disconnect power, wait 10 seconds, and reconnect.
	\item \textbf{Check storage space:}  
	Ensure there is enough free space on the main unit's microSD card.  
	Low storage can slow down performance or prevent new data from being saved.
\end{itemize}

%% --- To-Do image placeholder: backup demonstration ---
%\begin{figure}[h!]
%	\centering
%	\fbox{\parbox[c][4cm][c]{10cm}{
%			\centering \textbf{TODO: Future addition – Backup \& Maintenance Dashboard UI mockup.}}}
%	\caption{(To be added) Example of weekly backup process.}
%	\label{fig:todo_backup_image}
%\end{figure}
%
%% ==========================================================
%\subsection{Maintenance Schedule}
%
%%\begin{table}[h!]
%%	\centering
%%	\caption{Recommended Maintenance Schedule}
%%	\renewcommand{\arraystretch}{1.3}
%%	\begin{tabular}{|l|l|l|}
%%		\hline
%%		\textbf{Task} & \textbf{Frequency} & \textbf{Performed By} \\ \hline
%%		Clean device and camera lens & Monthly & Operator \\ \hline
%%		Check cable connections & Monthly & Operator \\ \hline
%%		Back up database & Weekly & Operator \\ \hline
%%		Update system software & Quarterly & Technician \\ \hline
%%		Inspect camera focus and lighting & Monthly & Operator \\ \hline
%%	\end{tabular}
%%\end{table}
%
%% ==========================================================
%
%\vspace{0.5cm}
%\noindent
%\textbf{Summary:}  
%Routine maintenance keeps the system stable, accurate, and long-lasting.  
%With regular cleaning, safe power use, and simple backups, the License Plate Detection System will continue operating reliably every day.