%%%%%%%%%%%%%%%%%%%%%%%%
%
% $Autor: Gautam Ramesh$
% $Datum: 2025-10-27 23:08:09Z $
% $Pfad: /Manual/Chapters/en/SafetyGuidelines.tex $
% $Version: 3 (Integrated Visuals)$
%
%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Safety Guidelines}

\section{Safety Guidelines}

The following safety guidelines are essential to ensure the reliable, secure, and fault-free operation of the \textbf{License Plate Detection System}. Failure to adhere to these protocols may result in hardware damage, data corruption, or safety hazards.

\vspace{0.5cm}

% --- INTEGRATED VISUAL SUMMARY ---
\begin{figure}[htbp]
	\centering
	\begin{tikzpicture}[
		font=\sffamily,
		% Styles
		safetyBox/.style={
			rectangle,
			rounded corners=5pt,
			minimum width=6.2cm,
			minimum height=4.2cm,
			text width=5.8cm,
			align=left,
			fill=white,
			draw=gray!30,
			thick,
			blur shadow={shadow blur steps=5},
			inner sep=8pt
		},
		header/.style={
			rectangle,
			rounded corners=3pt,
			minimum width=2.4cm,
			minimum height=0.7cm,
			text=white,
			font=\bfseries\small,
			align=center,
			blur shadow
		}
		]
		% Colors
		\definecolor{elecYellow}{RGB}{255, 190, 0}
		\definecolor{thermRed}{RGB}{220, 50, 50}
		\definecolor{opsBlue}{RGB}{0, 100, 180}
		\definecolor{mechGray}{RGB}{80, 80, 90}
		
		% QUADRANT 1: ELECTRICAL
		\node[safetyBox, draw=elecYellow] (elec) at (0,0) {
			\vspace{0.6cm}
			\begin{itemize}
				\item Use certified 5V/4A Power Supply.
				\item No hot-plugging (HDMI/Camera).
				\item Use surge protection devices.
				\item Inspect cable insulation daily.
			\end{itemize}
		};
		\node[header, fill=elecYellow, anchor=north west] at ($(elec.north west)+(0.2, -0.2)$) {ELECTRICAL};
		
		% QUADRANT 2: THERMAL
		\node[safetyBox, draw=thermRed, right=0.6cm of elec] (therm) {
			\vspace{0.6cm}
			\begin{itemize}
				\item Operational: 0$^\circ$C to 40$^\circ$C.
				\item Do NOT block heatsink vents.
				\item Active cooling required if $>40^\circ$C.
				\item Keep dry and away from humidity.
			\end{itemize}
		};
		\node[header, fill=thermRed, anchor=north west] at ($(therm.north west)+(0.2, -0.2)$) {THERMAL};
		
		% QUADRANT 3: OPERATIONAL
		\node[safetyBox, draw=opsBlue, below=0.6cm of elec] (ops) {
			\vspace{0.6cm}
			\begin{itemize}
				\item Always use \texttt{sudo poweroff}.
				\item Avoid forced hard reboots.
				\item Monitor logs during high AI load.
				\item Disconnect power before transit.
			\end{itemize}
		};
		\node[header, fill=opsBlue, anchor=north west] at ($(ops.north west)+(0.2, -0.2)$) {OPERATIONAL};
		
		% QUADRANT 4: MECHANICAL
		\node[safetyBox, draw=mechGray, right=0.6cm of ops] (mech) {
			\vspace{0.6cm}
			\begin{itemize}
				\item Use ESD Wrist Strap on PCB.
				\item Secure Camera mounting brackets.
				\item Prevent cable tension/strain.
				\item Use stable, level surface.
			\end{itemize}
		};
		\node[header, fill=mechGray, anchor=north west] at ($(mech.north west)+(0.2, -0.2)$) {MECHANICAL};
		
	\end{tikzpicture}
	\caption{Safety Protocol Matrix: Multi-domain operational constraints.}
	\label{fig:safety_matrix}
\end{figure}

\vspace{0.5cm}

\subsection{Electrical Safety}
The Jetson Nano is sensitive to voltage fluctuations. Strict adherence to power standards is required:
\begin{itemize}
	\item \textbf{Power Supply:} Always use a certified \textbf{5V / 4A USB-C power supply}. Undervoltage will cause the system to shut down unexpectedly during AI inference spikes.
	\item \textbf{Hot-Plugging:} Never connect or disconnect peripherals (Camera, HDMI) while the main unit is live. This can cause transient voltage spikes damaging the board's logic gates.
	\item \textbf{Cabling:} Regularly check cables for fraying. Ensure all connectors are fully seated and not loose.
	\item \textbf{Grounding:} Use surge-protected outlets to prevent static or grid spikes from reaching the board.
\end{itemize}

\subsection{Thermal and Mechanical Safety}
The system relies on a combination of passive aluminum heatsinks and optional active cooling.
\begin{itemize}
	\item \textbf{Ventilation:} Do not block the vents of the case. Ambient heat buildup can lead to thermal throttling, reducing the FPS of the detection engine.
	\item \textbf{Temperature Range:} Operating range is strictly \textbf{0\,\textdegree C to 40\,\textdegree C}. If deployed in gatehouses without climate control, active fan cooling is mandatory.
	\item \textbf{Liquids:} The board has no conformal coating; keep all liquids and conductive dust away.
	\item \textbf{ESD Protection:} Static electricity can kill a Maxwell GPU instantly. Use an anti-static wrist strap when opening the case.
\end{itemize}

\subsection{Operational Safety}
Software-level safety ensures the longevity of the file system and database.
\begin{itemize}
	\item \textbf{Shutdown Procedure:} Sudden power loss can corrupt the SQLite \texttt{parking.db} file. Always initiate a shutdown via the dashboard button or terminal.
	\item \textbf{Monitoring:} If the device exhibits abnormal fan noise or LED flickering, power off immediately.
	\item \textbf{Database Integrity:} Ensure database operations are finished before relocating the hardware to avoid write-errors on the SSD.
\end{itemize}

\subsection{Inference Safety}
Continuous AI processing generates cumulative heat. 
\begin{itemize}
	\item \textbf{Load Monitoring:} It is recommended to check the GPU load periodically. Avoid 100\% utilization in direct sunlight.
	\item \textbf{Cooling Breaks:} After 24 hours of continuous high-load testing, allow the device a short idle period to stabilize internal temperatures.
\end{itemize}