\chapter{Set Up}
\label{ch:system_setup}

\section{System Setup}

This section explains, in simple steps, how to prepare and start the \textbf {License Plate Detection System}.  
No technical knowledge is required — follow the setup steps below to get the system ready for use.

\vspace{0.4cm}
\noindent
\textbf{Step 1: Place and Connect the Hardware}
\begin{itemize}
	\item Place the \textbf{System} on a stable, well-ventilated surface.
	\item Mount the \textbf{camera} on its stand and point it toward the vehicle lane or entry gate.
	\item Connect the camera to the System using the USB port.
	\item Connect the \textbf{HDMI cable} from the Jetson Nano to the monitor.
	\item Plug in the \textbf{power adapter } but do not turn it on yet.
\end{itemize}

\vspace{0.3cm}
\noindent
\textbf{Step 2: Start the System}
\begin{itemize}
	\item Insert the \textbf{microSD card} (already loaded with JetPack 5.1.2).  
	\item Turn on the power switch.  
	\item Wait a few seconds for the system to start automatically.  
	\item The display will show the live camera view once it is ready.
\end{itemize}

\vspace{0.3cm}
\noindent
\textbf{Step 3: Verify Operation}
\begin{itemize}
	\item Watch the screen — detected number plates will appear automatically.
	\item Adjust the camera height or tilt if the plate is not clearly visible.
\item Ensure good lighting at the vehicle gate area.
For accurate plate reading, maintain an illumination level between 
\textbf{250 lux (minimum)} and \textbf{900 lux (maximum)} — with an 
optimal range of \textbf{400–700 lux}. 
Avoid shining lights directly into the camera to prevent glare or overexposure.
	\item The system saves every detection with date and time automatically.
\end{itemize}

\vspace{0.3cm}
\noindent
\textbf{Step 4: During and After Use}
\begin{itemize}
	\item The system runs continuously and does not need supervision.  
	\item After use, simply turn off the power supply.  
	\item All data is stored safely for later review or reporting.
\end{itemize}

\vspace{0.5cm}
\noindent
\textbf{System Setup Diagram:}

\begin{figure}[h!]
	\centering
	\resizebox{1.2\textwidth}{!}{%
		\begin{tikzpicture}[
			node distance=2.4cm, 
			>=stealth,
			font=\large,
			every node/.style={align=center}
			]
			
			% Define styles
			\tikzstyle{block} = [rectangle, draw=blue!70!black, fill=blue!10, 
			rounded corners, minimum height=1cm, minimum width=3.3cm, text centered, font=\small]
			\tikzstyle{process} = [rectangle, draw=green!60!black, fill=green!10, 
			rounded corners, minimum height=1cm, minimum width=3.6cm, text centered, font=\small]
			\tikzstyle{db} = [cylinder, shape border rotate=90, draw=orange!90!black, fill=orange!10, 
			minimum height=1.3cm, minimum width=1.1cm, aspect=0.4, font=\small]
			\tikzstyle{arrow} = [->, thick]
			
			% --- LAYER 1: Hardware devices ---
			\node[block] (camera) {\faCamera \\ \textbf{Camera}};
			\node[block, right=4.0cm of camera] (nano) {\faMicrochip \\ \textbf{System}\\};
			\node[block, right=4.0cm of nano] (display) {\faDesktop \\ \textbf{HDMI Display}};
			\node[block, below=1.7cm of nano, fill=gray!10, draw=gray!60!black] (power) {\faBolt \\ 5V / 4A USB-C Power Supply};
			
			% --- LAYER 2: Software / Processing pipeline ---
			\node[process, below=2cm of power, xshift=-3.9cm] (os) {\textbf{JetPack 5.1.2 (Ubuntu 20.04)}};
			\node[process, right=4.0cm of os] (yolo) {\textbf{YOLOv8 Detection}};
			\node[process, right=4.0cm of yolo] (ocr) {\textbf{EasyOCR Reading}};
			\node[db, below=2cm of yolo, yshift=-0.2cm] (database) {\textbf{SQLite}\\plates.db};
			
			% --- ARROWS: Hardware layer ---
			\draw[arrow] (camera) -- node[above, yshift=0.2cm]{\scriptsize Video Stream (USB)} (nano);
			\draw[arrow] (nano) -- node[above, yshift=0.2cm]{\scriptsize Output (HDMI)} (display);
			\draw[arrow] (power) -- node[right]{\scriptsize Power Input} (nano);
			
			% --- ARROWS: Software layer ---
			\draw[arrow, dashed, blue!80!black] (os) -- (yolo);
			\draw[arrow, dashed, blue!80!black] (yolo) -- (ocr);
			\draw[arrow, dashed, blue!80!black] (ocr) -- (database);
			
			% --- CONNECTIONS BETWEEN LAYERS ---
			\draw[arrow, thick, gray!70!black, bend right=20] (nano.south) to (os.north);
			\draw[arrow, thick, orange!80!black, bend left=20] (database.north) to (display.south);
			
			% --- DECORATIVE BOXES ---
			\node[draw=blue!40!black, thick, rounded corners, fit=(camera)(nano)(display)(power), label={[yshift=0.2cm]above:\textbf{Hardware Layer(Main setup)}}] {};
			\node[draw=green!40!black, thick, rounded corners, fit=(os)(yolo)(ocr)(database), label={[yshift=-0.3cm]below:\textbf{Software and Data Flow Layer(Backend)}}] {};
			
		\end{tikzpicture}%
	}
	\caption{System setup overview – hardware and software working together.}
	\label{fig:setup_complex_tikz}
\end{figure}
\begin{center}
	\textbf{\textcolor{red}{TODO: This diagram will be removed in the future}}
\end{center}

\vspace{0.4cm}
\noindent
\vspace{0.4cm}
\noindent
\vspace{0.3cm}
\noindent
\textbf{Note:}  
The upper part of Figure~\ref{fig:setup_complex_tikz} shows the \textbf{outer hardware setup}

The lower part represents the \textbf{internal processing layer}, which runs automatically inside the System.  
It includes the system software, detection model, and database used for number plate recognition and data storage.  
This section is mainly relevant for developers who want to understand or extend the system’s logic.