%%%%%%%%%%%%
%
% $Autor: Wings $
% $Datum: 2019-03-05 08:03:15Z $
% $Pfad: Troubleshooting.tex $
% $Version: 4250 $
% !TeX spellcheck = en_GB/de_DE
% !TeX encoding = utf8
% !TeX root = manual 
% !TeX TXS-program:bibliography = txs:///biber
%
%%%%%%%%%%%%

\chapter{Troubleshooting}
\section{Troubleshooting}

The following section lists the most common problems that may arise during the operation of the \textbf{License Plate Detection System} and their possible causes and solutions.  
These checks help maintain system stability, reduce downtime, and ensure uninterrupted plate detection.

% ==========================================================
\subsection{Hardware and Power Issues}

\begin{itemize}
	\item \textbf{System Does Not Power On:}  
	\begin{itemize}
		\item Verify that the 5 V/4 A USB-C adapter is properly connected and the LED indicator on the Jetson Nano is on.  
		\item Try a different power cable or wall adapter.  
		\item Avoid powering the device through unpowered USB hubs.
	\end{itemize}
	
	\item \textbf{Jetson Overheating or Shutting Down Unexpectedly:}  
	\begin{itemize}
		\item Check for adequate ventilation or add a small 5 V fan.  
		\item Use the command \texttt{sudo tegrastats} to monitor temperature.  
		\item Keep the operating environment below 40 °C.
	\end{itemize}
	
	\item \textbf{Camera Not Detected:}  
	\begin{itemize}
		\item Run \texttt{ls /dev/video*} to verify if the camera is recognized.  
		\item If not listed, re-insert the camera or test it on another PC.  
		\item Ensure the correct USB port is used (avoid low-power front ports).
	\end{itemize}
\end{itemize}

\begin{figure}[h!]
	\centering
	\begin{tikzpicture}[>=stealth, thick, node distance=1.5cm]
		\tikzstyle{block}=[rectangle, draw=gray!70!black, fill=gray!10, rounded corners, text width=4.2cm, align=center, minimum height=1cm]
		\tikzstyle{arrow}=[->, thick]
		
		\node[block] (start) {No Power / Camera Issue Detected};
		\node[block, below=of start] (check1) {Check Power Adapter and Cable};
		\node[block, below=of check1] (check2) {Verify USB Connections};
		\node[block, below=of check2] (check3) {Run \texttt{ls /dev/video*}};
		\node[block, below=of check3] (resolve) {Reboot or Replace Faulty Unit};
		
		\draw[arrow] (start) -- (check1);
		\draw[arrow] (check1) -- (check2);
		\draw[arrow] (check2) -- (check3);
		\draw[arrow] (check3) -- (resolve);
	\end{tikzpicture}
	\caption{Basic hardware troubleshooting flow.}
	\label{fig:hardware_troubleshoot}
\end{figure}

% ==========================================================
% ==========================================================
\subsection{Software and Model Issues}

\begin{itemize}
	\item \textbf{YOLOv8 Model Fails to Load:}  
	\begin{itemize}
		\item Check that the weight file (\texttt{best.pt}) is in the correct path.  
		\item Reinstall Ultralytics using \texttt{pip install ultralytics --upgrade}.  
		\item Ensure dependencies (\texttt{torch}, \texttt{onnxruntime}, \texttt{cv2}) are up to date.
	\end{itemize}
	
	\item \textbf{Low Frame Rate (FPS):}  
	\begin{itemize}
		\item Switch to a lighter model like YOLOv8-Nano or reduce camera resolution to 640×480.  
		\item Use \texttt{sudo nvpmodel -m 0} and \texttt{sudo jetson\_clocks} to maximize Jetson performance.  
		\item Avoid running other GPU-intensive tasks in the background.
	\end{itemize}
	
	\item \textbf{OCR Produces Incorrect Text:}  
	\begin{itemize}
		\item Clean the camera lens and ensure proper lighting.  
		\item Adjust contrast or threshold parameters in preprocessing.  
		\item Retrain the OCR model with localized license plate fonts.
	\end{itemize}
\end{itemize}
% ==========================================================
\subsection{Database and Storage Issues}

\begin{itemize}
	\item \textbf{Database Locked Error:}  
	\begin{itemize}
		\item Close any other process accessing \texttt{plates.db}.  
		\item Use \texttt{sqlite3 plates.db "PRAGMA journal\_mode=WAL;"} to enable safer writes.  
		\item Restart the app to release the file handle.
	\end{itemize}
	
	\item \textbf{Database File Missing or Corrupted:}  
	\begin{itemize}
		\item Restore the latest backup (\texttt{sqlite3 plates.db < backup.sql}).  
		\item Ensure sufficient SD card space (use \texttt{df -h}).  
		\item Avoid abrupt power cuts while writing to the database.
	\end{itemize}
	
	\item \textbf{Storage Running Full:}  
	\begin{itemize}
		\item Delete old logs in \texttt{/logs/}.  
		\item Run \texttt{sudo apt clean} and clear unused packages.  
		\item Expand the SD card partition if necessary.
	\end{itemize}
\end{itemize}

% ==========================================================
\subsection{Network or Communication Issues}

\begin{itemize}
	\item \textbf{SSH Connection Fails:}  
	\begin{itemize}
		\item Verify the IP address using \texttt{ifconfig} or \texttt{hostname -I}.  
		\item Ensure SSH is enabled: \texttt{sudo systemctl enable ssh}.  
		\item Check firewall settings or router restrictions.
	\end{itemize}
	
	\item \textbf{Data Not Syncing Across Multiple Units:}  
	\begin{itemize}
		\item Confirm all devices have the same network time (use \texttt{ntpdate}).  
		\item Test connectivity via \texttt{ping <IP>}.  
		\item Use a centralized database or MQTT broker for multi-unit setups.
	\end{itemize}
\end{itemize}

% ==========================================================
\subsection*{Troubleshooting Reference Table}

\begin{table}[h!]
	\centering
	\caption{Common Issues, Causes, and Solutions}
	\begin{tabular}{|p{3.5cm}|p{4cm}|p{6cm}|}
		\hline
		\textbf{Problem} & \textbf{Possible Cause} & \textbf{Solution} \\ \hline
		No power or LED off & Faulty adapter or cable & Replace power supply and check connections \\ \hline
		Camera not detected & Loose USB or bad port & Reconnect or test with another PC \\ \hline
		Model not loading & Missing weight file & Re-download or verify file path \\ \hline
		Low FPS & High resolution or throttling & Reduce resolution / enable performance mode \\ \hline
		Database locked & Concurrent access & Restart app / enable WAL mode \\ \hline
		OCR errors & Poor lighting or angle & Improve illumination / refocus camera \\ \hline
		System overheating & Blocked airflow & Add fan or reposition device \\ \hline
	\end{tabular}
\end{table}

% ==========================================================
\subsection*{Summary}

The majority of operational issues can be resolved through systematic checks on power, software dependencies, and database integrity.  
Using diagnostic commands like \texttt{tegrastats}, \texttt{lsusb}, and \texttt{sqlite3} greatly simplifies fault identification.  
Following these troubleshooting procedures minimizes downtime and ensures that the License Plate Detection System continues to function reliably in continuous deployment environments.







