%%%%%%
%
% $Autor: Wings $
% $Datum: 2020-01-18 11:15:45Z $
% $Pfad: WuSt/Skript/Produktspezifikation/powerpoint/ImageProcessing.tex $
% $Version: 4620 $
%
%%%%%%


\chapter{First Steps}

\section{Find your Way Around}

\begin{itemize}
    \item Lesen Sie das Jetson Nano Developer Kit-Benutzerhandbuch \cite{JetsonUserGuide:2019}, das Folgendes enthält: 
    \begin{itemize}
        \item Mehr Details über die Hardware des Developer Kits.
        \item Erklärungen aller Komponenten von NVIDIA JetPack, einschließlich Entwicklertools mit Unterstützung für die Cross-Compilation.
        \item Lists aller enthaltenen Muster und Musterdokumentation.
    \end{itemize}
    \item Gehen Sie zur \href{https://developer.nvidia.com/jetson}{NVIDIA Jetson Developer Zone}, um Zugang zu allen Informationen der Jetson-Plattform zu erhalten.
    \item Fragen stellen oder ein Projekt in den \href{https://devtalk.nvidia.com/default/board/372/jetson-projects/}{NVIDIA Jetson Foren} teilen. 
\end{itemize}


\section{Projects and Learning}

The Jetson Nano Developer Kit is an AI computer for learning and creating.

\section{Take the free NVIDIA Deep Learning course}

In the self-paced online course for beginners, you will learn to collect image data and use it to train, optimise and deploy AI models for custom tasks such as hand gesture recognition and image regression to locate a key point in an image. \href{https://courses.nvidia.com/courses/course-v1:DLI+C-RX-02+V1/about}{Subscribe Now!}


\section{Visit \href{https://developer.nvidia.com/embedded/community/jetson-projects}{Jetson Projects Page}}

\begin{itemize}
    \item \href{https://developer.nvidia.com/embedded/twodaystoademo#hello_ai_world}{Hello AI World}
    \begin{itemize}
        \item Start with Deep Learning inference for computer vision with pre-trained models for image classification and object recognition.
\item Real-time acceleration with TensorRT and live camera streaming.
\item Create your own recognition program in C++.
\item For those interested in training their own networks, attend two days of demo that includes both training and inference.
    \end{itemize}
    
    \item \href{https://github.com/NVIDIA-AI-IOT/jetbot}{JetBot} is an open source AI project for makers, students and enthusiasts interested in learning AI and developing fun applications. 
    \begin{itemize}
    \item It is easy to set up and use and compatible with many popular accessories.
    \item Several interactive tutorials show you how to harness the power of AI to teach JetBot to follow objects, avoid collisions and more.
    \item JetBot is a great starting place for creating entirely new AI projects.
  \end{itemize}
\end{itemize}


\section{Create your own Projects}

\begin{itemize}
  \item The Jetson Nano Developer Kit provides useful tools, such as the \href{https://github.com/NVIDIA/jetson-gpio}{Jetson GPIO Python Library}, and is compatible with common sensors and peripherals, including many from Adafruit and Raspberry Pi.
  \item Many popular AI frameworks such as TensorFlow, PyTorch, Caffe and MXNet are supported, and Jetson Nano is capable of running multiple neural networks in parallel to process data and drive actions.
\end{itemize}


