%%%%%%
%
% $Autor: Wings $
% $Datum: 2020-11-07 15:09:45Z $
% $Pfad: GDV/Vortraege/latex - Ausarbeitung/Kapitel/Appendix.tex $
% $Version: 4749 $
%
%%%%%%




\chapter{Criteria for a good \LaTeX{} project}


A good report is not only characterised by good content, but also fulfils formal aspects. The following list should help to comply with basic rules. Before submitting, all points should be checked and ticked off.


\begin{todolist}
    \item Is a suitable directory structure used?
    \item Is an appropriate division into files used?
    \item Are meaningful directory and file names used?
    \begin{todolist}
        \item Are directory and file names such as report or term paper avoided?
        \item Are meaningful names used for images and not \glqq image1\grqq?
        \item Are directory and file names not too long?
        \item Are special characters and spaces avoided?
    \end{todolist}
    \item Are commands like \textcolor{red}{\textbackslash newline} and \textcolor{red}{\textbackslash\textbackslash} avoided?
    \item Are the \LaTeX files clearly laid out?
    \begin{todolist}
        \item Are indentations used in the \LaTeX files?
        \item Are free lines inserted?
        \item Is the project mentioned in the header of the files?
        \item Does the header of the files mention the main sources?
        \item Is the author mentioned in the header of the files?
    \end{todolist}
    \item Are all necessary files given?
    \item Are the temporary files deleted?
    \item Are graphics created by yourself?
    \item Are the sources of the images given?
    \item Are citations made with the command \textcolor{red}{\textbackslash cite}?
    \item Is a bib file used?
    \item Are the entries of the bib-file clearly arranged? 
    \item Are the entries of the bib-file edited to show them correctly?
    \item Are the correct types used for the bib entries?
    \item Are meaningful keys used in the bib files?
\end{todolist}

\bigskip

Unfortunately, the list cannot be complete, but it provides some clues.