%%%%%%%%%%%%%%%%%%%%%%%%
% $Autor: RanjeetsingTawar$
% $Pfad: Car_Licence_Plate_Identification_with_a_JetsonNano$
% $Version: 4.0.0 $
%
% !TeX encoding = utf8
%
%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Libraries/Packages List}

	\section{Introduction}
	
	Data science has become a cornerstone of modern industries, transforming operations across sectors such as finance, healthcare, retail, and beyond. The exponential growth in data generation over the past decade has created a pressing demand for robust tools that can manage and analyze vast, complex datasets with precision and efficiency. This surge has fueled the development of powerful data science packages that streamline tasks such as data manipulation, visualization, and machine learning.
	
	These packages have become indispensable for data scientists, equipping them with the tools needed to process raw data, uncover meaningful patterns, and build predictive models. By leveraging these tools, businesses can derive actionable insights, optimize decision-making, and maintain a competitive edge in an increasingly data-driven world.
	
	In this context, the report highlights some of the most widely used data science packages, including pandas, numpy, matplotlib, datetime, seaborn, keras, lightgbm, and tensorflow. These packages are open-source, feature-rich, and supported by extensive documentation, making them user-friendly for both beginners and seasoned professionals. Their capabilities range from handling structured data efficiently to developing sophisticated machine learning models, underscoring their critical role in the data science ecosystem.
	
		\section{Pandas}
	
	The term "pandas" is derived from "panel data", which is an econometrics term used for datasets that consist of observations over multiple time periods for the same individuals. [\cite{McKinney:2011}] The name "pandas" is a clever play on words, combining the words "Python data analysis" with the econometrics term. [\cite{McKinney:2012}] Pandas is a data manipulation package that allows for the analysis of tabular data. It provides functionality for cleaning, merging, and transforming data. Pandas is built on top of the numpy package and allows for the easy manipulation of dataframes and series.
	
	\begin{lstlisting}[language=Python]
		
		import pandas as pd
		
	\end{lstlisting}
	
	\section{Numpy}
	
	NumPy is a powerful Python package that serves as the foundation for scientific computing and data analysis. It provides a multidimensional array object, along with a comprehensive set of functions and tools for working with arrays. NumPy's array structure allows for efficient storage and manipulation of large datasets, enabling fast numerical computations and mathematical operations. Its vast collection of mathematical functions, including linear algebra, Fourier transforms, and random number generation, makes it an indispensable tool for scientific and data-intensive applications \cite{McKinney:2012}. NumPy's simplicity, performance, and integration with other scientific libraries have made it the go-to choice for professionals and researchers in fields such as physics, engineering, finance, and machine learning.
	
	\begin{lstlisting}[language=Python]
		
		import Numpy as np
		
	\end{lstlisting}
	
	\section{Matplotlib}
	
	Matplotlib is a comprehensive Python package that facilitates 2D plotting and generates high-quality graphs suitable for use in professional settings. It supports both interactive and non-interactive plotting and can save output images in multiple formats such as PNG. Additionally, it offers an array of plot types, including lines, bars, pie charts, and histograms, among others. Matplotlib is highly customizable, flexible, and user-friendly \cite{Hunter:2007}.
	
	\begin{lstlisting}[language=Python]
		
		import matplotlib.pyplot as plt
		
	\end{lstlisting}
	
		\section{Datetime}
	
	Datetime is a package that provides functionality for working with dates and times. It allows for the easy manipulation of dates and times, including arithmetic operations and formatting. Datetime is often used in conjunction with pandas to manipulate date and time data.
	
	\section{Keras}
	
	Keras is a user-friendly, high-level Python library for deep learning that can be integrated with TensorFlow, Theano, or CNTK. It allows developers to focus on the essential aspects of deep learning, such as designing neural network layers, without worrying about the complex mathematical details of tensors and their shapes. TensorFlow, Theano, or CNTK must be used as the back-end for Keras. With Keras, users can develop deep learning applications without directly interacting with the intricacies of the underlying framework.
	Keras offers two primary APIs: the sequential API and the functional API. The sequential API is based on the concept of a sequence of layers, making it the most common and straightforward use of Keras. The sequential model is a linear stack of layers, where each layer is added in sequence, allowing for easy construction of a neural network model.
	
		\section{TensorFlow}
	
	TensorFlow is an open-source machine learning library developed by the Google Brain team. Keras is an open-source high-level neural networks API, written in Python and capable of running on top of TensorFlow.
	
	TensorFlow is used as the main machine learning framework, and Keras provides a high-level API for building and training neural networks. The layers module from Keras is used for defining layers in the neural network \cite{TensorFlow:2023}.
	
	\begin{lstlisting}[language=Python]
		
		import tensorflow as tf
		from tensorflow import keras
		from tensorflow.keras import layers
		
	\end{lstlisting}
	
	\section{Imagedataset}
	
	A utility function in TensorFlow/Keras that loads and preprocesses image datasets from a directory. This is used to load and preprocess image data efficiently, simplifying the process of setting up the dataset for training.
	
	\begin{lstlisting}[language=Python]
		
		from tensorflow.keras.preprocessing import image_dataset_from_directory 
		
	\end{lstlisting}
	
