%%%%%%%%%%%%
%
% $Autor: Wings $
% $Datum: 2019-03-05 08:03:15Z $
% $Pfad: Maintenance.tex $
% $Version: 4250 $
% !TeX spellcheck = en_GB/de_DE
% !TeX encoding = utf8
% !TeX root = manual 
% !TeX TXS-program:bibliography = txs:///biber
%
%%%%%%%%%%%%

\chapter{Troubleshooting}

This chapter provides solutions for common issues that may arise while using the Vehicle License Plate Detection System with the Jetson Nano.

\section{System Not Powering On}
\begin{itemize}[label=--, left=1.5em]
	\item \textbf{Check Power Connection:} Ensure the power adapter is securely connected to the Jetson Nano and that the power supply is functional.
	\item \textbf{Confirm Power Specifications:} Verify that you are using a 5V/3A adapter, as inadequate power may prevent startup.
\end{itemize}

\section{Camera Not Detected}
\begin{itemize}[label=--, left=1.5em]
	\item \textbf{Verify Camera Connection:} Confirm the camera is properly connected to the designated port on the Jetson Nano.
	\item \textbf{Install Required Drivers:} Ensure camera drivers are installed. Run \texttt{sudo apt-get install v4l-utils} if necessary.
\end{itemize}

\section{LED Indicator Not Activating}
\begin{itemize}[label=--, left=1.5em]
	\item \textbf{Check GPIO Setup:} Confirm that the LED is connected to the correct GPIO pin and that the pin setup in your code matches the physical connection.
	\item \textbf{Test GPIO Output:} Run a simple GPIO test script to verify that the pin outputs correctly.
\end{itemize}

\section{Model Failing to Detect License Plates}
\begin{itemize}[label=--, left=1.5em]
	\item \textbf{Verify Model Path:} Ensure the detection model file is correctly loaded in your script and that the path is accurate.
	\item \textbf{Check Input Dimensions:} Ensure the input image dimensions are compatible with the model’s requirements. Adjust the camera feed size if necessary.
\end{itemize}

\section{Low Detection Accuracy}
\begin{itemize}[label=--, left=1.5em]
	\item \textbf{Lighting Conditions:} Ensure adequate lighting for the camera feed, as poor lighting can affect detection.
	\item \textbf{Adjust Model Settings:} Fine-tune model parameters or consider retraining the model with additional data for improved accuracy.
\end{itemize}

For issues beyond these troubleshooting steps, consult the Jetson Nano documentation or support forums for additional assistance.




